### 2022-03-23 draft.Rmd
March 23 After Class. Created initial visualization and worked with other data.

---
title: "final_project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Political Donations
```{r}
library(tidyverse)
library(ggthemes)
pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
pol_donations <- pol_donations %>% rename(year = 'Election Year')
```

```{r}
pol_donations 
nfl <- pol_donations %>% filter(League == "NFL") 
nfl %>% group_by(Party) %>%
  summarise(n = n())
```

```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(desc(n))) %>%
  filter(rank <= 25) %>%
  mutate(owner = fct_reorder(.f = Owner, .x = n))

ggplot(data = owner_rank, aes(x = owner, y = n)) +
  geom_point(size=5, color="red", fill=alpha("orange", 0.3), alpha=0.7, shape=21, stroke=2) +
  geom_segment(aes(x = owner, xend = owner, y = 0, yend = n)) +
  coord_flip() +
    labs(title = "Most Frequent Donators Among All Leagues",
       y = "Count",
       x = "Owners") +
  theme_fivethirtyeight() 
```

## Blockbusters
```{r}
library(tidyverse)
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters

ggplot(data = blockbusters, aes(x = release_year, y = length_in_min)) +
  geom_line()
```

## History of Rock
```{r}
library(tidyverse)
history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")

history_of_rock %>%

led <- history_of_rock %>% filter(artist == "Led Zeppelin")

ggplot(data = led, aes(x = release_date, y = popularity)) +
  geom_line() 
```

## Unemployment

```{r}
unemployment_data_us <- read_csv("data/unemployment_data_us.csv")
unemployment_data_us
```

### 2022-03-28 draft.Rmd
March 28 graded before class commit. Made a few visualizations.

@@
 ---
-title: "final_project"
+title: "final_project_draft"
 output: html_document
@@
 
-## Political Donations
-```{r}
+## Political Donations of Professional Sports Team Owners 
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
 library(tidyverse)
@@
 pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
-pol_donations <- pol_donations %>% rename(year = 'Election Year')
+pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) 
+library(plotly)
 ```
 
-```{r}
-pol_donations 
-nfl <- pol_donations %>% filter(League == "NFL") 
-nfl %>% group_by(Party) %>%
-  summarise(n = n())
+## Owners Who Donate The Most Frequently and How Much 
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+owner_rank <- pol_donations %>% group_by(Owner, League) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+frequent <- pol_donations %>% group_by(Owner) %>%
+    mutate(n = n()) %>%
+    filter(n >= 65) %>%
+  arrange(n) %>%
+  mutate(donations = as.numeric(n)) %>%
+  mutate(order = fct_reorder(.f = Owner, .x = donations))
+
+plot1 <- ggplot(data = frequent, aes(x = amount, y = order, label = Amount, colour = League)) +
+  geom_point() +
+  labs(title = "Owners Who Have Made the Most Donations",
+       y = "Owners",
+       x = "Amount Donated",
+       colour = "League") +
+  theme_fivethirtyeight() +
+  scale_colour_brewer(palette = "Dark2")
+
+ggplotly(plot1, tooltip = "label") 
 ```
 
+## Top 25 Highest Political Donations by NFL Team Owners in 2016 
 ```{r, message = FALSE, warning = FALSE, echo = FALSE}
-owner_rank <- pol_donations %>% group_by(Owner) %>%
-  summarise(n = n()) %>%
-  arrange(desc(n)) %>%
-  mutate(rank = rank(desc(n))) %>%
-  filter(rank <= 25) %>%
-  mutate(owner = fct_reorder(.f = Owner, .x = n))
+high_donations <- pol_donations %>% filter(year == "2016" & League == "NFL") %>%
+  mutate(amount = parse_number(Amount)) %>%
+  arrange(desc(amount)) %>%
+  mutate(Rank = rank(desc(amount))) %>%
+  filter(Rank <= 25) %>%
+  mutate(owner_ordered = fct_reorder(.f = Owner, .x = amount)) %>%
+  mutate(party = fct_relevel(Party, c("Republican", "Democrat", "Bipartisan")))
 
-ggplot(data = owner_rank, aes(x = owner, y = n)) +
-  geom_point(size=5, color="red", fill=alpha("orange", 0.3), alpha=0.7, shape=21, stroke=2) +
-  geom_segment(aes(x = owner, xend = owner, y = 0, yend = n)) +
-  coord_flip() +
-    labs(title = "Most Frequent Donators Among All Leagues",
-       y = "Count",
-       x = "Owners") +
-  theme_fivethirtyeight() 
+plot2 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
+  geom_point() +
+  labs(x = "Amount Donated",
+       y = "Owner",
+       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
+       colour = "Political Party",
+       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
+  theme_fivethirtyeight()  +
+  scale_colour_manual(values = c("red", "blue", "yellow"))
+
+ggplotly(plot2, tooltip = "label") 
 ```
@@
 ## Blockbusters
-```{r}
-library(tidyverse)
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+library(ggrepel)
 blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
 blockbusters
+```
 
-ggplot(data = blockbusters, aes(x = release_year, y = length_in_min)) +
-  geom_line()
+## 5 Highest & Lowest IMBD Ratings Highlighted by Title
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+blockbusters %>% group_by(mpaa_rating) %>%
+  summarise(n = n())
+
+blockbusters1 <- blockbusters %>% filter(!is.na(mpaa_rating))
+
+interest <- blockbusters1 %>% mutate(rank = rank(desc(imdb_rating))) %>%
+  select(rank, everything()) %>%
+  arrange(rank) %>%
+  slice(1:5)
+
+interest2 <- blockbusters1 %>% mutate(rank = rank(imdb_rating)) %>%
+  select(rank, everything()) %>%
+  arrange(rank) %>%
+  slice(1:5)
+
+ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating)) +
+  geom_point() +
+  geom_label_repel(data = interest, aes(label = film_title), show.legend = FALSE) +
+  geom_label_repel(data = interest2, aes(label = film_title), show.legend = FALSE) +
+   geom_point(data = interest, size = 3, shape = 1, show.legend = FALSE) +
+   geom_point(data = interest2, size = 3, shape = 1, show.legend = FALSE) +
+  labs(y = "IMDB Rating",
+       x = "Release Year",
+       colour = "MPAA Rating",
+       title = "Blockbuster Ratings: 1977 to 2019",
+       subtitle = "5 Highest & Lowest IMBD Ratings Highlighted by Title") +
+  theme_fivethirtyeight() +
+  scale_colour_brewer(palette = "Dark2")
 ```
@@
 ## History of Rock
-```{r}
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
 library(tidyverse)
 history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")
+history_of_rock
+```
 
-history_of_rock %>%
+## Most Popular Nirvana Songs 
+```{r}
+history_of_rock %>% group_by(artist) %>%
+  summarise(n = n()) %>% arrange(desc(n))
 
-led <- history_of_rock %>% filter(artist == "Led Zeppelin")
+nirvana <- history_of_rock %>% filter(artist == "Nirvana") %>% arrange(desc(popularity)) %>%
+  mutate(order = fct_reorder(.f = name, .x = popularity)) %>%
+  rename(Release_Date = 'release_date')
+nirvana %>% select(order, everything())
 
-ggplot(data = led, aes(x = release_date, y = popularity)) +
-  geom_line() 
+plot3 <- ggplot(data = nirvana, aes(x = popularity, y = order, label = Release_Date)) +
+  geom_point() +
+  geom_segment(aes(x = popularity, xend = popularity, y = 0, yend = order)) +
+  coord_flip() +
+  labs(x = "Popularity",
+       y = "Song Title",
+       title = "Most Popular Nirvana Songs")
+
+ggplotly(plot3, tooltip = "label")
 ```
@@
 ## Unemployment
-
 ```{r}

### 2022-03-28 draft.Rmd
March 28 graded after class commit. Fixed lollipop graph and made table.

@@
 pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) 
+pol_donations
 library(plotly)
-```
-
-## Owners Who Donate The Most Frequently and How Much 
-```{r, message = FALSE, warning = FALSE, echo = FALSE}
-owner_rank <- pol_donations %>% group_by(Owner, League) %>%
-  summarise(n = n()) %>%
-  arrange(desc(n))
-
-frequent <- pol_donations %>% group_by(Owner) %>%
-    mutate(n = n()) %>%
-    filter(n >= 65) %>%
-  arrange(n) %>%
-  mutate(donations = as.numeric(n)) %>%
-  mutate(order = fct_reorder(.f = Owner, .x = donations))
-
-plot1 <- ggplot(data = frequent, aes(x = amount, y = order, label = Amount, colour = League)) +
-  geom_point() +
-  labs(title = "Owners Who Have Made the Most Donations",
-       y = "Owners",
-       x = "Amount Donated",
-       colour = "League") +
-  theme_fivethirtyeight() +
-  scale_colour_brewer(palette = "Dark2")
-
-ggplotly(plot1, tooltip = "label") 
 ```
@@
 
-plot2 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
+plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
   geom_point() +
@@
 
+ggplotly(plot1, tooltip = "label") 
+```
+
+## Owners Who Donate The Most Frequently and How Much 
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+owner_rank <- pol_donations %>% group_by(Owner, League) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+frequent <- pol_donations %>% group_by(Owner) %>%
+    mutate(n = n()) %>%
+    filter(n >= 65) %>%
+  arrange(desc(n)) %>%
+  mutate(donations = as.numeric(n))
+
+test <- frequent %>% mutate(owner = fct_reorder(.f = Owner, .x = n))
+test2 <- frequent %>% mutate(owner = fct_inorder(Owner))
+
+plot2 <- ggplot(data = test2, aes(x = amount, y = owner, label = Amount, colour = League)) +
+  geom_point() +
+  labs(title = "Owners Who Have Made the Most Donations",
+       y = "Owners",
+       x = "Amount Donated",
+       colour = "League") +
+  theme_fivethirtyeight() +
+  scale_colour_brewer(palette = "Dark2")
+
 ggplotly(plot2, tooltip = "label") 
+```
+
+## Going off Second Political Donations Visualization
+```{r}
+library(knitr)
+library(pander)
+library(tidyverse)
+
+owner_rank2 <- pol_donations %>% group_by(Owner, Team) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n)) %>%
+  filter(n >= 65)
+
+kable(owner_rank2, caption = "Frequency of Donations",
+      col.names = c("Owner", "Team", "Amount of Donations Made"))
+```
+
+## Examining Top Donator 
+```{r}
+charles_johnson <- pol_donations %>% filter(Owner == "Charles Johnson") %>%
+  filter(year == 2016 | year == 2018 | year == 2020)
+
+ggplot(data = charles_johnson, aes(x = amount)) +
+  geom_freqpoly()
+
+charles_johnson %>% group_by(Recipient, amount) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+ggplot(data = charles_johnson, aes(x = amount, y = ))
 ```
@@
 
-plot3 <- ggplot(data = nirvana, aes(x = popularity, y = order, label = Release_Date)) +
+plot3 <- ggplot(data = nirvana, aes(x = order, y = popularity, label = popularity, colour = popularity)) +
   geom_point() +
-  geom_segment(aes(x = popularity, xend = popularity, y = 0, yend = order)) +
+  geom_segment(aes(x = order, xend = order, y = 0, yend = popularity)) +
   coord_flip() +
-  labs(x = "Popularity",
-       y = "Song Title",
-       title = "Most Popular Nirvana Songs")
+  labs(title = "Most Popular Nirvana Songs",
+       colour = "Popularity") +
+  theme_fivethirtyeight() +
+  scale_colour_viridis_b()
 

### 2022-03-30 draft.Rmd
March 30 graded after class commit. Created a few simple visualizations.

--- 2022-03-23 draft.Rmd
@@
 
-## Political Donations
-```{r}
+## Political Donations of Professional Sports Team Owners 
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
 library(tidyverse)
 library(ggthemes)
+
 pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
-pol_donations <- pol_donations %>% rename(year = 'Election Year')
+
+pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) %>% 
+  mutate(Recipient = fct_recode(Recipient, Hillary_Victory_Fund = "HILLARY VICTORY FUND", 
+                                Hillary_Victory_Fund = "Hillary Victory Fund",
+                                Office_Of_Commissioner_of_MLB_PAC = "Office of the Commissioner of Major League Baseball PAC",
+                                Office_Of_Commissioner_of_MLB_PAC = "OFFICE OF THE COMMISSIONER OF MAJOR LEAGUE BASEBALL POLITICAL ACTION COMMITTEE"))
+
+library(plotly)
+```
+
+## Top 25 Highest Political Donations by NFL Team Owners in 2016 
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+high_donations <- pol_donations %>% filter(year == "2016" & League == "NFL") %>%
+  mutate(amount = parse_number(Amount)) %>%
+  arrange(desc(amount)) %>%
+  mutate(Rank = rank(desc(amount))) %>%
+  filter(Rank <= 25) %>%
+  mutate(owner_ordered = fct_reorder(.f = Owner, .x = amount)) %>%
+  mutate(party = fct_relevel(Party, c("Republican", "Democrat", "Bipartisan")))
+
+plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
+  geom_point() +
+  labs(x = " ", 
+       y = " ",
+       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
+       colour = "Political Party",
+       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
+  scale_colour_viridis_d()
+
+ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
+  geom_point() +
+  labs(x = " ", 
+       y = " ",
+       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
+       colour = "Political Party",
+       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
+  scale_colour_viridis_d()
+
+    scale_x_discrete("Amount Donated", labels = abbreviate)
+
+scale_x_discrete(breaks = c("0e+00", "1e+05", "2e+05", "3e+05", "4e+05"),
+                  labels = c("0", "100", "200", "300", "400"))
+
+ggplotly(plot1, tooltip = "label") 
+```
+
+## Owners Who Donate The Most Frequently and How Much 
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+owner_rank <- pol_donations %>% group_by(Owner, League) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+frequent <- pol_donations %>% group_by(Owner) %>%
+  mutate(n = n()) %>%
+  filter(n >= 65) %>%
+  arrange(desc(n)) %>%
+  mutate(donations = as.numeric(n))
+
+ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
+  geom_point() +
+  labs(title = "Owners Who Have Made the Most Donations",
+       y = "Owners",
+       x = "Amount Donated",
+       colour = "League") +
+  theme_hc() +
+  scale_colour_viridis_d()
+
+plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
+  geom_point() +
+  labs(title = "Owners Who Have Made the Most Donations",
+       y = "Owners",
+       x = "Amount Donated",
+       colour = "League") +
+  theme_hc() +
+  scale_colour_viridis_d()
+
+ggplotly(plot2, tooltip = "label")
+
+test <- frequent %>% mutate(owner = fct_reorder(.f = Owner, .x = n))
+test2 <- frequent %>% mutate(owner = fct_inorder(Owner))
+```
+
+## Going off Second Political Donations Visualization
+```{r}
+library(knitr)
+library(pander)
+library(tidyverse)
+
+owner_rank2 <- pol_donations %>% group_by(Owner, Team) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n)) %>%
+  filter(n >= 65)
+
+kable(owner_rank2, caption = "Frequency of Donations from 2016 to 2020",
+      col.names = c("Owner", "Team", "Amount of Donations Made"))
+```
+
+## Examining Top Donator 
+```{r}
+library(ggthemes)
+charles_johnson <- pol_donations %>% filter(Owner == "Charles Johnson") %>%
+  filter(year == 2016 | year == 2018 | year == 2020)
+
+cj_party <- charles_johnson %>% group_by(Party) %>%
+  summarise(n = n()) %>%
+  mutate(party = fct_reorder(.f = Party, .x = n)) %>%
+  mutate(Party = fct_relevel(party, c("Republican", "Bipartisan, but mostly Republican",
+                                        "Democrat")))
+
+ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
+  geom_col() +
+  coord_flip() +
+  scale_fill_viridis_d() +
+  labs(title = "Count of Donations",
+       x = "Political Party",
+       y = "Count") +
+  theme_hc()
 ```
@@
 ```{r}
-pol_donations 
-nfl <- pol_donations %>% filter(League == "NFL") 
-nfl %>% group_by(Party) %>%
-  summarise(n = n())
+owner_rank2
 ```
 
-```{r, message = FALSE, warning = FALSE, echo = FALSE}
-owner_rank <- pol_donations %>% group_by(Owner) %>%
+## Organizations Receiving Most Donations Across All Leagues
+```{r}
+recipients <- pol_donations %>% group_by(Recipient, Party) %>%
   summarise(n = n()) %>%
   arrange(desc(n)) %>%
-  mutate(rank = rank(desc(n))) %>%
-  filter(rank <= 25) %>%
-  mutate(owner = fct_reorder(.f = Owner, .x = n))
+  filter(n >= 15) %>%
+  ungroup() %>%
+  mutate(recipient = fct_reorder(.f = Recipient, .x = n)) %>%
+  mutate(Party = fct_relevel(Party, c("Bipartisan", "Republican", "Democrat")))
 
-ggplot(data = owner_rank, aes(x = owner, y = n)) +
-  geom_point(size=5, color="red", fill=alpha("orange", 0.3), alpha=0.7, shape=21, stroke=2) +
-  geom_segment(aes(x = owner, xend = owner, y = 0, yend = n)) +
+ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
+  geom_point() +
+  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
   coord_flip() +
-    labs(title = "Most Frequent Donators Among All Leagues",
-       y = "Count",
-       x = "Owners") +
-  theme_fivethirtyeight() 
+  labs(x = "Recipients",
+       y = "Count") +
+  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
+  theme_hc() +
+  scale_colour_brewer(palette = "Dark2")
 ```
@@
 ## Blockbusters
-```{r}
-library(tidyverse)
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
 blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
 blockbusters
+```
 
-ggplot(data = blockbusters, aes(x = release_year, y = length_in_min)) +
-  geom_line()
+## Blockbuster Ratings: 1977 to 2019
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
+blockbusters %>% group_by(mpaa_rating) %>%
+  summarise(n = n())
+
+blockbusters1 <- blockbusters %>% filter(!is.na(mpaa_rating)) %>%
+  rename(Film = 'film_title')
+
+plot6 <- ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
+                                          label = Film)) +
+  geom_point() +
+  labs(y = "IMDB Rating",
+       x = "Release Year",
+       colour = "MPAA Rating",
+       title = "Blockbuster Ratings: 1977 to 2019") +
+  theme_hc() +
+  scale_colour_brewer(palette = "Dark2")
+
+ggplotly(plot6, tooltip = "label")
+```
+
+## 
+```{r}
+blockbusters
+
+interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
+  select(rank, everything()) %>%
+  arrange(rank) %>%
+  slice(1:5) %>%
+  mutate(film_title = fct_recode(film_title, 
+                                 LOTR_The_Return_Of_The_King = "The Lord of the Rings: The Return of the King",
+                                 LOTR_Fellowship_Of_The_Ring = "The Lord of the Rings: The Fellowship of the Ring"))
+interest
+
+interest2 <- blockbusters %>% mutate(rank = rank(imdb_rating)) %>%
+  select(rank, everything()) %>%
+  arrange(rank) %>%
+  slice(1:5)
+interest2
+
+library(ggrepel)
+ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
+  geom_point() +
+  geom_label_repel(data = interest, aes(label = film_title)) +
+  geom_point(data = interest2, aes(x = release_year, y = domestic_gross)) +
+  geom_label_repel(data = interest2, aes(label = film_title))
+
+ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
+  geom_hex() +
+  labs(x = "Release Year",
+       y = "Film Budget") 
 ```
@@
 ## History of Rock
-```{r}
+```{r, message = FALSE, warning = FALSE, echo = FALSE}
 library(tidyverse)
 history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")
-
-history_of_rock %>%
-
-led <- history_of_rock %>% filter(artist == "Led Zeppelin")
-
-ggplot(data = led, aes(x = release_date, y = popularity)) +
-  geom_line() 
+history_of_rock
 ```
 
-## Unemployment
+## Most Popular Nirvana Songs 
+```{r}
+history_of_rock %>% group_by(artist) %>%
+  summarise(n = n()) %>% arrange(desc(n))
+
+nirvana <- history_of_rock %>% rename(Popularity = 'popularity') %>%
+  filter(artist == "Nirvana") %>% arrange(desc(Popularity)) %>%
+  mutate(order = fct_reorder(.f = name, .x = Popularity)) %>%
+  rename(Release_Date = 'release_date')
+
+nirvana %>% select(order, everything())
+
+plot3 <- ggplot(data = nirvana, aes(x = order, y = Popularity, label = Popularity, colour = Popularity)) +
+  geom_point() +
+  geom_segment(aes(x = order, xend = order, y = 0, yend = Popularity)) +
+  coord_flip() +
+  labs(title = "Most Popular Nirvana Songs",
+       colour = "Popularity", 
+       x = " ",
+       y = " ") +
+  theme_hc() +
+  scale_colour_viridis_b()
+
+ggplotly(plot3, tooltip = "label")
+```
 
 ```{r}
-unemployment_data_us <- read_csv("data/unemployment_data_us.csv")
-unemployment_data_us
+beatles <- history_of_rock %>% filter(artist == "The Beatles")
+
+plot10 <- ggplot(data = beatles, aes(x = release_date, y = popularity)) +
+  geom_line() +
+  geom_point() +
+  labs(x = "Release Date",
+       y = "Popularity")
+
+ggplotly(plot10, tooltip = "label")
+
+beatles %>% arrange(desc(popularity)) 
 ```
+
+## Unemployment Data Set
+```{r}
+library(lubridate)
+unemployment <- read_csv("data/unemployment_data_us.csv")
+ggplot(data = unemployment, aes(x = Date, y = Professional_Degree)) +
+  geom_point()
+```

### 2022-04-04 draft.Rmd
April 4th graded before class commit.

@@
        y = " ",
-       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
-       colour = "Political Party",
-       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
-  scale_colour_viridis_d()
+       title = "What Influence Could NFL Team Owners Have on Elections?",
+       colour = "Political Party") +
+  scale_colour_viridis_d() +
+  theme_bw()
+
+ggplotly(plot1, tooltip = "label")
 
@@
        colour = "Political Party",
-       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
-  scale_colour_viridis_d()
-
-    scale_x_discrete("Amount Donated", labels = abbreviate)
-
-scale_x_discrete(breaks = c("0e+00", "1e+05", "2e+05", "3e+05", "4e+05"),
-                  labels = c("0", "100", "200", "300", "400"))
-
-ggplotly(plot1, tooltip = "label") 
+       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
+  scale_colour_viridis_d() +
+  theme_bw()
 ```
 
-## Owners Who Donate The Most Frequently and How Much 
+## Table of Owners Who Make the Most Donations
+```{r}
+library(knitr)
+library(pander)
+library(tidyverse)
+library(kableExtra)
+
+owner_rank2 <- pol_donations %>% group_by(Owner, Team, League) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n)) %>%
+  filter(n >= 65)
+
+kable(owner_rank2, caption = "Who Makes the Most Donations Across All Leagues?",
+      col.names = c("Owner", "Team", "League", "Amount of Donations Made")) %>%
+  kable_classic()
+```
+
+## How Much Do They Donate? 
 ```{r, message = FALSE, warning = FALSE, echo = FALSE}
@@
 
-ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
+ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
   geom_point() +
-  labs(title = "Owners Who Have Made the Most Donations",
+  labs(title = "How Much Do They Donate?",
        y = "Owners",
        x = "Amount Donated",
-       colour = "League") +
-  theme_hc() +
-  scale_colour_viridis_d()
+       colour = "Party") +
+  scale_colour_brewer(palette = "Dark2") +
+  theme(legend.position = "bottom")
 
-plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
+plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Recipient, colour = Party)) +
   geom_point() +
-  labs(title = "Owners Who Have Made the Most Donations",
+  labs(title = "How Much Do They Donate & To Who?",
        y = "Owners",
        x = "Amount Donated",
-       colour = "League") +
-  theme_hc() +
-  scale_colour_viridis_d()
+       colour = "Party") +
+  theme_grey() +
+  scale_colour_brewer(palette = "Dark2") +
+  theme(legend.position = "bottom")
 
@@
 test2 <- frequent %>% mutate(owner = fct_inorder(Owner))
-```
-
-## Going off Second Political Donations Visualization
-```{r}
-library(knitr)
-library(pander)
-library(tidyverse)
-
-owner_rank2 <- pol_donations %>% group_by(Owner, Team) %>%
-  summarise(n = n()) %>%
-  arrange(desc(n)) %>%
-  filter(n >= 65)
-
-kable(owner_rank2, caption = "Frequency of Donations from 2016 to 2020",
-      col.names = c("Owner", "Team", "Amount of Donations Made"))
 ```
@@
   scale_fill_viridis_d() +
-  labs(title = "Count of Donations",
+  labs(title = "Count of Donations by Political Party?",
        x = "Political Party",
        y = "Count") +
-  theme_hc()
+  theme(legend.position = "bottom") +
+  geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 
 ```
 
+## What Are Some of These Organizations? 
 ```{r}
-owner_rank2
+organizations <- charles_johnson %>% group_by(Recipient, Party) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n)) %>%
+  filter(n >= 2)
+
+kable(organizations, caption = "What Are Some Organizations Charles Johnson Donates To?",
+      col.names = c("Recipient", "Political Party", "Amount of Donations Made"))  %>%
+  kable_classic()
 ```
@@
   labs(title = "Organizations Receiving Most Donations Across All Leagues") +
-  theme_hc() +
-  scale_colour_brewer(palette = "Dark2")
+  theme_bw() +
+  scale_colour_brewer(palette = "Dark2") +
+  theme(legend.position = "bottom")
 ```
 
-## Blockbusters
+## Blockbusters: A blockbuster is a Hollywood movie that's made with a large budget and big stars.
+A true blockbuster is extremely popular and brings in a lot of money (https://www.vocabulary.com/dictionary/blockbuster).
 ```{r, message = FALSE, warning = FALSE, echo = FALSE}
@@
 
-## 
+## Has the Budget for Blockbusters Increased Throughout Time? 
+```{r}
+ggplot(data = blockbusters, aes(x = release_year, y = film_budget, colour = release_year)) +
+  geom_point() +
+  geom_smooth(se = FALSE, method = "lm") +
+  labs(x = "Release Year",
+       y = "Film Budget",
+       title = "Has the Budget for Blockbusters Increased Throughout Time?",
+       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
+  theme_bw() +
+  scale_colour_viridis_c() +
+  theme(legend.position = "none")
+
+ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
+  geom_hex() +
+  geom_smooth(se = FALSE, method = "lm") +
+  labs(x = "Release Year",
+       y = "Film Budget", 
+       title = "Has the Budget for Blockbusters Increased Throughout Time?",
+       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
+  theme_bw() 
+```
+
+## Which American/Domestic Distributor Has Produced the Most Blockbusters 1977-2019
+```{r}
+blockbusters3 <- blockbusters %>% group_by(domestic_distributor) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n)) %>%
+  mutate(order = fct_reorder(.f = domestic_distributor, .x = n)) %>%
+  filter(!n == 1)
+
+ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
+  geom_col() +
+  coord_flip() +
+  geom_label(data = blockbusters3, aes(label = n), show.legend = FALSE) +
+  labs(x = "Amount of Films Produced",
+       y = "Domestic Distributor",
+       title = "Amount of Blockbusters Produced by Domestic Distributors: 1977-2019") +
+  theme_bw() +
+  theme(legend.position = "none")
+```
+
+## Work in Progress 
 ```{r}
@@
   geom_label_repel(data = interest2, aes(label = film_title))
-
-ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
-  geom_hex() +
-  labs(x = "Release Year",
-       y = "Film Budget") 
 ```
@@
   coord_flip() +
-  labs(title = "Most Popular Nirvana Songs",
+  labs(title = "Most Popular Nirvana Songs: 1991-2018",
        colour = "Popularity", 
@@
        y = " ") +
-  theme_hc() +
-  scale_colour_viridis_b()
+  theme_bw() +
+  scale_colour_viridis_b() +
+  theme(legend.position = "none")
 
@@
 
+## Trying to Make Density Ridges Plot 
 ```{r}
-beatles <- history_of_rock %>% filter(artist == "The Beatles")
+## install.packages("ggridges")
+library(ggridges)
 
-plot10 <- ggplot(data = beatles, aes(x = release_date, y = popularity)) +
+nirvana_small <- nirvana %>% slice(1:5) %>%
+  mutate(order = fct_reorder(.f = name, .x = valence))
+ggplot(data = nirvana_small, aes(x = order, y = valence)) +
+  geom_density_ridges() +
+  coord_flip() +
+  labs(x = "Title",
+       y = "Valence")
+```
+
+## Works in Progress - Simple Visualizations
+```{r}
+nirvana_line <- nirvana %>% rename(Title = 'name')
+plot10 <- ggplot(data = nirvana_line, aes(x = Release_Date, y = Popularity, label = Title)) +
   geom_line() +
-  geom_point() +
+  geom_point(colour = "darkolivegreen") +
   labs(x = "Release Date",
-       y = "Popularity")
+       y = "Popularity",
+       title = "Comparing Popularity by Release Date") +
+  theme_bw() +
+  theme(legend.position = "none")
 
@@
 
-beatles %>% arrange(desc(popularity)) 
+table <- history_of_rock %>% group_by(artist) %>%
+  summarise(mean = mean(popularity)) %>%
+  arrange(desc(mean)) %>%
+  slice(1:10)
+
+top10 <- history_of_rock %>% arrange(desc(popularity)) %>% slice(1:10)
 ```

### 2022-04-04 draft.Rmd
April 4th graded after class commit. Worked with theme() in ggplot.

@@
        y = " ",
-       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
+       title = "How Much Did NFL Owners Donate in 2016?",
        colour = "Political Party",
@@
   scale_colour_viridis_d() +
-  theme_bw()
+  theme_bw() +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 9.5),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     size = 8),
+        legend.title = element_text(family = "mono",
+                                    face = "bold",
+                                    size = 8),
+        legend.text = element_text(family = "mono",
+                                   size = 8),
+        axis.text = element_text(family = "mono",
+                                 size = 8),
+        legend.box.background = element_rect())
 ```
@@
 
-kable(owner_rank2, caption = "Who Makes the Most Donations Across All Leagues?",
-      col.names = c("Owner", "Team", "League", "Amount of Donations Made")) %>%
-  kable_classic()
+kable(owner_rank2, caption = "<b>Who Makes the Most Donations Across All Leagues?<b>", format = "html",
+      col.names = c("Owner", "Team", "League", "Donations Made")) %>%
+  kable_styling(html_font = "Cambria", bootstrap_options = "striped",
+                font_size = 9) 
 ```
@@
   geom_point() +
-  labs(title = "How Much Do They Donate?",
-       y = "Owners",
-       x = "Amount Donated",
+  labs(title = "How Many Donations Have They Made?",
+       subtitle = "Examining The Monetary Amount of Observed Political Donations",
+       y = " ",
+       x = " ",
        colour = "Party") +
   scale_colour_brewer(palette = "Dark2") +
-  theme(legend.position = "bottom")
+    theme_bw() +
+  theme(legend.position = "bottom",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 12),
+        axis.text.x = element_text(family = "mono"),
+        axis.text.y = element_text(family = "mono"),
+        legend.title = element_text(family = "mono", 
+                                    face = "bold",
+                                    size = 5),
+        legend.text = element_text(family = "mono",
+                                   size = 5),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     size = 9),
+        legend.box.background = element_rect())
 
@@
   labs(title = "Count of Donations by Political Party?",
-       x = "Political Party",
-       y = "Count") +
-  theme(legend.position = "bottom") +
+       x = " ",
+       y = " ") +
+  theme(legend.position = "bottom",
+        plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        legend.title = element_text(family = "mono",
+                                    face = "bold"),
+        legend.text = element_text(family = "mono")) +
   geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 

### 2022-04-06 draft.Rmd
April 6th graded before class commit. Worked more with theme() and changed a few things.

--- 2022-04-04 draft.Rmd
@@
 ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
-  geom_point() +
+  geom_point(size = 3) +
   labs(x = " ", 
        y = " ",
-       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
+       title = "How Much Did NFL Owners Donate in 2016?",
        colour = "Political Party",
@@
   scale_colour_viridis_d() +
-  theme_bw()
+  theme_bw() +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 15,
+                                  margin = margin(c(t = 20,
+                                                    b = 50,
+                                                    vjust = 10))),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     size = 10),
+        legend.title = element_text(family = "mono",
+                                    face = "bold",
+                                    size = 8),
+        legend.text = element_text(family = "mono",
+                                   size = 8),
+        axis.text = element_text(family = "mono",
+                                 size = 8),
+        legend.box.background = element_rect(),
+        legend.position = "bottom")
 ```
@@
   geom_point() +
-  labs(title = "How Much Do They Donate?",
-       y = "Owners",
-       x = "Amount Donated",
+  labs(title = "How Many Donations Have They Made?",
+       subtitle = "Examining The Monetary Amount of Observed Political Donations",
+       y = " ",
+       x = " ",
        colour = "Party") +
   scale_colour_brewer(palette = "Dark2") +
-  theme(legend.position = "bottom")
+    theme_bw() +
+  theme(legend.position = "bottom",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 12,
+                                  margin = margin(c(t = 50,
+                                                    b = 50)),
+                                  vjust = 10),
+        axis.text.x = element_text(family = "mono"),
+        axis.text.y = element_text(family = "mono"),
+        legend.title = element_text(family = "mono", 
+                                    face = "bold",
+                                    size = 7),
+        legend.text = element_text(family = "mono",
+                                   size = 6),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     size = 9,
+                                     vjust = 5),
+        legend.box.just = "left",
+        legend.box.background = element_rect())
 
@@
   scale_fill_viridis_d() +
-  labs(title = "Count of Donations by Political Party?",
-       x = "Political Party",
-       y = "Count") +
-  theme(legend.position = "bottom") +
-  geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 
+  labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
+       x = " ",
+       y = "Count of Donations") +
+  theme(legend.position = "bottom",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  hjust = 0.5,
+                                  size = 13,
+                                  margin = margin(c(t = 50,
+                                                    b = 50)),
+                                  vjust = 10),
+        axis.text = element_text(family = "mono"),
+        legend.title = element_text(family = "mono",
+                                    face = "bold"),
+        legend.text = element_text(family = "mono"),
+        axis.ticks.y = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title.x = element_text(family = "mono",
+                                    size = 9,
+                                    face = "italic",
+                                    margin = margin(t = 20))) +
+  geom_label(data = cj_party, aes(label = n), show.legend = FALSE,
+             label.size = 1)
 ```
@@
 
-kable(organizations, caption = "What Are Some Organizations Charles Johnson Donates To?",
+kable(organizations, caption = "<b>What Are Some Organizations Charles Johnson Donates To?<b>",
       col.names = c("Recipient", "Political Party", "Amount of Donations Made"))  %>%
-  kable_classic()
+  kable_styling(html_font = "Cambria", bootstrap_options = "striped",
+                font_size = 15) %>%
+  scroll_box(height = "500px")
 ```
@@
 
+new_names <- c("Collins For Senator", "McSally for Senate Inc.",
+               "ActBlue", "Portman For Senate Committee", "NRCC",
+               "NRSC", "Hillary Victory Fund", "Team Ryan", 
+               "Office of the Commissioner of MLB PAC", "Gridirion PAC")
+
 ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
@@
   coord_flip() +
-  labs(x = "Recipients",
-       y = "Count") +
+  labs(x = " ",
+       y = "Count of Donations") +
   labs(title = "Organizations Receiving Most Donations Across All Leagues") +
-  theme_bw() +
   scale_colour_brewer(palette = "Dark2") +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  scale_x_discrete(labels = new_names) +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  margin = margin(c(t = 50,
+                                                    b = 50)),
+                                  vjust = 10),
+        axis.text = element_text(family = "mono"),
+        axis.title = element_text(family = "mono",
+                                  size = 8),
+        axis.title.x = element_text(size = 10,
+                                    margin = margin(t = 20,
+                                                    b = 10)),
+        legend.title = element_text(family = "mono",
+                                    face = "bold"),
+        legend.text = element_text(family = "mono"),
+        axis.ticks = element_blank(),
+         legend.box.background = element_rect())
 ```
@@
 
-plot6 <- ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
+plot6
+
+ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                           label = Film)) +
   geom_point() +
+  facet_wrap(~mpaa_rating) +
+  geom_smooth(se = FALSE, method = 'lm') +
   labs(y = "IMDB Rating",
@@
   theme_hc() +
-  scale_colour_brewer(palette = "Dark2")
-
-ggplotly(plot6, tooltip = "label")
+  scale_colour_brewer(palette = "Dark2") +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "italic",
+                                  margin = margin(t = 20, b = 20)),
+        axis.ticks = element_blank(),
+        axis.title = element_text(family = "mono",
+                                  face = "italic"),
+        axis.text = element_text(family = "mono"),
+        legend.box.background = element_rect(),
+        legend.text = element_text(family = "mono"),
+        legend.title = element_text(family = "mono",
+                                    face = "italic"),
+        axis.title.y = element_text(margin = margin(r = 20)),
+        axis.title.x = element_text(margin = margin(t = 20, b = 10)),
+        strip.text = element_text(family = "mono",
+                                  face = "bold"))
 ```
@@
   geom_point() +
-  geom_smooth(se = FALSE, method = "lm") +
+  geom_smooth(se = FALSE, method = "lm", colour = "black") +
   labs(x = "Release Year",
        y = "Film Budget",
-       title = "Has the Budget for Blockbusters Increased Throughout Time?",
-       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
+       title = "Has the Budget for Blockbuster Films Increased Throughout Time?",
+       subtitle = "Film Budget for Blockbusters: 1977-2019") +
   theme_bw() +
   scale_colour_viridis_c() +
-  theme(legend.position = "none")
-
-ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
-  geom_hex() +
-  geom_smooth(se = FALSE, method = "lm") +
-  labs(x = "Release Year",
-       y = "Film Budget", 
-       title = "Has the Budget for Blockbusters Increased Throughout Time?",
-       subtitle = "Film Budget for Blockbuesters: 1977-2019") +
-  theme_bw() 
+  theme(legend.position = "none",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  margin = margin(c(t = 50, b = 50)),
+                                  vjust = 10),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     vjust = 5),
+        axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        axis.ticks = element_blank(),
+        axis.title.x = element_text(margin = margin(c(l = 20))),
+        axis.title.y = element_text(margin = margin(c(t = 20, b = 20, r = 20)))) 
+## need to add more to this visualization 
 ```
@@
 ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
-  geom_col() +
+  geom_point() +
+  geom_segment(aes(x = order, xend = order, y = 0, yend = n)) +
   coord_flip() +
@@
   theme_bw() +
-  theme(legend.position = "none")
+  theme(legend.position = "none",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  margin = margin(c(t = 50)),
+                                  vjust = 10),
+        axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        axis.text.y = element_text(face = "italic"),
+        axis.ticks = element_blank(),
+        axis.title.x = element_text(margin = margin(c(b = 20))),
+        axis.title.y = element_text(margin = margin(c(t = 30, r = 30))))
 ```
@@
 blockbusters
-
 interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
@@
 ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
-  geom_point() +
+  geom_point(aes(colour = imdb_rating)) +
   geom_label_repel(data = interest, aes(label = film_title)) +
-  geom_point(data = interest2, aes(x = release_year, y = domestic_gross)) +
+  geom_point(data = interest2, aes(x = release_year, y = domestic_gross, colour = imdb_rating)) +
   geom_label_repel(data = interest2, aes(label = film_title))

### 2022-04-06 draft.Rmd
April 6th graded after class commit. Made a few improvements.

@@
 library(plotly)
+options(scipen = 10)
+## install.packages("ggpmisc")
+library(ggpmisc)
 ```
@@
 
-plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
-  geom_point() +
-  labs(x = " ", 
-       y = " ",
-       title = "What Influence Could NFL Team Owners Have on Elections?",
-       colour = "Political Party") +
-  scale_colour_viridis_d() +
-  theme_bw()
-
-ggplotly(plot1, tooltip = "label")
-
 ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
-  geom_point(size = 3) +
+  geom_point(size = 2) +
   labs(x = " ", 
@@
 
-ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
+level_order <- factor(frequent$Owner, level = c('Stephen M. Ross', 'Herbert Simon',
+                                                'Jerry Reinsdorf', 'Ken Kendrick',
+                                                'Jimmy and Susan Haslam',
+                                                'Jody Allen (Paul G. Allen Trust)',
+                                                'Dan DeVos', 'John Rogers',
+                                                'Micky Arison', 'Charles Johnson'))
+
+ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
   geom_point() +
@@
         legend.box.background = element_rect())
-
-plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Recipient, colour = Party)) +
-  geom_point() +
-  labs(title = "How Much Do They Donate & To Who?",
-       y = "Owners",
-       x = "Amount Donated",
-       colour = "Party") +
-  theme_grey() +
-  scale_colour_brewer(palette = "Dark2") +
-  theme(legend.position = "bottom")
-
-ggplotly(plot2, tooltip = "label")
-
-test <- frequent %>% mutate(owner = fct_reorder(.f = Owner, .x = n))
-test2 <- frequent %>% mutate(owner = fct_inorder(Owner))
 ```
@@
 
+level_order2 <- factor(charles_johnson$Party, level = c('Republican', 'Democrat', 'Bipartisan, but mostly Republican'))
+
 ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
@@
   coord_flip() +
-  scale_fill_viridis_d() +
+  scale_fill_viridis_d(option = "plasma") +
   labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
@@
                                     face = "italic",
-                                    margin = margin(t = 20))) +
-  geom_label(data = cj_party, aes(label = n), show.legend = FALSE,
-             label.size = 1)
+                                    margin = margin(t = 20)))
+
+table <- data.frame(Party = rep(c("Republican", "Bipartisan, but mostly Republican",
+                                "Democrat", each = 1),
+                              Count = rep(c("207", "4", "2"), 1)))
+table
+
+ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
+  geom_col() + 
+  annotate(geom = "table") +
+  coord_flip()
 ```
@@
        y = "Count of Donations") +
-  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
+  labs(title = "Organizations Receiving Most Donations Among All Owners") +
   scale_colour_brewer(palette = "Dark2") +
@@
          legend.box.background = element_rect())
+
+pol_donations %>% group_by(League) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
 ```
@@
   rename(Film = 'film_title')
-
-plot6
 
@@
                                   face = "bold"))
+
+blockbusters %>% group_by(mpaa_rating) %>%
+  summarise(n = n()) %>%
+  filter(!is.na(mpaa_rating))
 ```

### 2022-04-13 draft.Rmd
April 13th graded before class commit. Made some changes and worked with new data set.

@@
 ```
+
+## Written Description 
+The general purpose of this project is to curate many different data visualizations using a variety of data sets.
+I want to create a personal website using blogdown to share these data visualizations.
+I decided to use data that was interesting to me, and found that I was most interested in data examining the political donations made by professional sport team owners from different leagues.
+
+Data Ethics: 
+* Political donations are public information; scraped the data from Kaggle, did not realize until today (April 10th) that fivethirtyeright actually published a piece using this data but luckily the visualizations that I have already made are different from those on fivethirtyeight
+* did not exclude N/A for a party affiliation point because I did not think there was any reason other than making the legend look better
+
+Expressing Variability:
+* Use scatter plots to show variability in data, and use bar plots to show the count of categorical variables
+
+Motivation and Grammar of Graphics:
+* Used theme() for the style of my visualizations
 
@@
   scale_fill_viridis_d(option = "plasma") +
-  labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
+  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
        x = " ",
@@
 
-table <- data.frame(Party = rep(c("Republican", "Bipartisan, but mostly Republican",
-                                "Democrat", each = 1),
-                              Count = rep(c("207", "4", "2"), 1)))
-table
+cj_party2 <- cj_party %>% select(n, party)
 
@@
 
-ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
-  geom_point() +
-  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
+ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
+  geom_col() +
   coord_flip() +
@@
   labs(title = "Organizations Receiving Most Donations Among All Owners") +
-  scale_colour_brewer(palette = "Dark2") +
+  scale_fill_brewer(palette = "Dark2") +
   theme(legend.position = "bottom") +
@@
   arrange(desc(n))
+```
+
+## Forbes Billionaires 2021
+
+## Potential questions:
+## Who are the most recent top 10 billionaires: name v net worth ?
+
+## look at average age of billionaires in general/maybe by country?: do billionaires tend to be very old or are there more billionaires on the younger side?
+
+## Look at most prevalent industry of billionaires: mostly technology or something else?
+
+## How many billionaires in each country: mostly capitalist or other economic systems?
+
+## Average networth of billionaires by industry?
+
+## Top 10 Billionaires coloured by industry (Forbes 2021 Billionaires)
+```{r}
+billionaires <- read_csv("data/Billionaire.csv")
+billionaires
+
+top10 <- billionaires %>% filter(Rank <= 10) %>%
+  mutate(NetWorth = parse_number(NetWorth)) %>%
+  mutate(order = fct_reorder(.f = Name, .x = NetWorth)) %>%
+  mutate(Industry = fct_relevel(Industry, c("Technology",
+                                            "Automotive",
+                                            "Fashion & Retail", 
+                                            "Finance & Investments", 
+                                            "Diversified")))
+top10
+
+new_names2 <- c("Mukesh Ambani", "Sergey Brin", "Larry Page", "Larry Ellison",
+                "Warren Buffett", "Mark Zuckerberg", "Bill Gates", 
+                "Bernard Arnault & Family", "Elon Musk", "Jeff Bezos")
+
+ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
+  geom_col() +
+  coord_flip() +
+  labs(x = "Billionaire Name", 
+       y = "Net Worth",
+       caption = "Measured in Billions",
+       colour = "Industry",
+       title = "2021 Forbes Billionaires with the Highest Net Worth") +
+  scale_fill_viridis_d() +
+  scale_x_discrete(labels = new_names2) +
+  theme(axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        axis.ticks = element_blank(),
+        plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        legend.title = element_text(family = "mono",
+                                    face = "bold"),
+        legend.text = element_text(family = "mono",
+                                   face = "italic"),
+        plot.caption = element_text(family = "mono",
+                                    face = "italic"))
+```
+
+## Forbes Billionaire 2021 2.0 Data Set
+```{r}
+forbes_billionaires <- read_csv("data/forbes_billionaires.csv")
+forbes_billionaires
+
+country <- forbes_billionaires %>% group_by(Country) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+country
+
+forbes_billionaires_age <- forbes_billionaires %>%
+  mutate(age = as.numeric(Age)) %>%
+  select(age, everything())
+
+countries_10 <- forbes_billionaires_age %>% filter(Country == "United States" |
+           Country == "China" |
+           Country == "India" |
+           Country == "Germany" |
+           Country == "Russia" |
+           Country == "Hong Kong" |
+           Country == "Brazil" |
+           Country == "Canada" |
+           Country == "United Kingdom" |
+           Country == "Italy")
+
+ggplot(data = countries_10, aes(x = Country, y = age)) +
+  geom_point() +
+  coord_flip()
+
+check <- countries_10 %>% filter(Age < 25 | Age > 90)
+
+filter <- countries_10 %>% filter(!is.na(age))
+filter2 <- filter %>% group_by(Country) %>%
+  summarise(Average = mean(age))
+
+ggplot(data = countries_10, aes(x = Country, y = age)) +
+  geom_point(alpha = 0.2) +
+  coord_flip() +
+  geom_point(data = filter2, aes(y = Average, colour = "Mean Age"),
+             size = 2.5) +
+  scale_colour_manual(values = c("Mean Age" = "red")) +
+  labs(x = "Country", 
+       y = "Age",
+       title = "Average Age of Billionaires by Country",
+       caption = "The Red Points Indicate the Average Age of Billionaires From Each
+       Country") +
+  theme(axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.ticks = element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(family = "mono",
+                                   face = "italic"),
+        legend.position = "none",
+        plot.caption = element_text(family = "mono",
+                                    size = 9,
+                                    face = "italic")) 
+```
+
+## Playing Around with New Variables 
+```{r}
+self_made <- forbes_billionaires %>% group_by(Self_made) %>%
+  summarise(n = n())
+
+ggplot(data = forbes_billionaires, aes(x = Self_made)) +
+  geom_bar()
+
+industry <- billionaires %>% group_by(Industry) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+industry
+
+combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))
+combined_billionaires
+
+usa_billionaires <- combined_billionaires %>% filter(Country.x == "United States")
+ggplot(data = usa_billionaires, aes(x = Self_made)) +
+  geom_bar()
+
+forbes_billionaires %>% group_by(Status) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+tidy_education <- forbes_billionaires %>% 
+  separate(col = Education, into = c("Degree", "University"),
+                                 sep = ", ") %>%
+  select(Degree, University, everything())
+tidy_education
+
+tidy_education %>% group_by(Degree) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+tidy_education2 <- tidy_education %>% filter(Degree == "Bachelor of Arts/Science" |
+                          Degree == "Master of Business Administration" |
+                          Degree == "Master of Science" |
+                          Degree == "Drop Out" |
+                          Degree == "Bachelor of Science" |
+                          Degree == "Bachelor of Science in Engineering" |
+                          Degree == "Doctorate" |
+                          Degree == "Diploma" |
+                          Degree == "Bachelor of Arts/Economic")
+
+ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
+  geom_point() +
+  coord_flip() +
+  labs(x = "Education Level",
+       y = "Net Worth")
+```
+
+## Forbes Billionaire 2021 3.0 Data Set 
+```{r}
+forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
+forbes_billionaires_geo 
+```
+
+## Billionaires Age in Countries with most billionaires 
+```{r}
+
+ggplot(data = countries_10, aes(x = Country, y = Age)) +
+  geom_point() +
+  coord_flip() +
+  geom_point(data = average_top10_countries, aes(y = Average, colour = "Average Billionaire Age")) +
+  scale_colour_manual(values = c("Average Billionaire Age" = "red"))
 ```

### 2022-04-18 draft.Rmd
April 18th graded before class commit. Got rid of some things but added new visualizations as well.

@@
 options(scipen = 10)
-## install.packages("ggpmisc")
 library(ggpmisc)
+library(ggrepel)
 ```
 
-## Top 25 Highest Political Donations by NFL Team Owners in 2016 
+## Questions: What were the highest 25 Political Donations made by NFL team owners in 2016?
+Were the majority of these donations affiliated with a certain party?
+How much influence could NFL team owners have on elections?
+Is there any gender that dominates?
 ```{r, message = FALSE, warning = FALSE, echo = FALSE}
@@
 
-## Table of Owners Who Make the Most Donations
+## Questions: Which owners, across all leagues, have made the most political donations from this data set? How many have they made? Is there a certain gender that dominates? 
 ```{r}
@@
 
-## How Much Do They Donate? 
+## Questions: How much money was spent for these donations?
+Do these donations tend to be made to the same party for each owner or do they vary?
+What is the total sum of the donations made by these individuals?
+What is the average amount per donation?
 ```{r, message = FALSE, warning = FALSE, echo = FALSE}
@@
   mutate(donations = as.numeric(n))
+
+frequent %>% group_by(Party) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+average_donation <- frequent %>% group_by(Owner) %>%
+  mutate(mean = mean(amount))
+average_donation
+
+ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
+  geom_point() +
+  geom_point(data = average_donation, aes(x = mean, colour = "Mean")) +
+  scale_colour_manual(values = c("Mean" = "Red"))
 
@@
   scale_colour_brewer(palette = "Dark2") +
+    theme_bw() +
+  theme(legend.position = "bottom",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 12),
+        axis.text.x = element_text(family = "mono"),
+        axis.text.y = element_text(family = "mono"),
+        legend.title = element_text(family = "mono", 
+                                    face = "bold",
+                                    size = 5),
+        legend.text = element_text(family = "mono",
+                                   size = 5),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     size = 9),
+        legend.box.background = element_rect())
+
+ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
+  geom_point() +
+  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
+  labs(title = "How Many Donations Have They Made?",
+       subtitle = "Examining The Monetary Amount of Observed Political Donations",
+       y = " ",
+       x = " ",
+       colour = "Party") +
+  scale_colour_brewer(palette = "Dark2") +
+  scale_colour_manual(values = c("Mean Donations" = "red")) +
     theme_bw() +
@@
         legend.box.background = element_rect())
+
+ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
+  geom_point() +
+  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
+  labs(title = "How Many Donations Have They Made?",
+       subtitle = "Examining The Monetary Amount of Observed Political Donations",
+       y = " ",
+       x = " ",
+       colour = "Party") +
+  scale_colour_viridis_d() +
+    theme_bw() +
+  theme(legend.position = "bottom",
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 12,
+                                  margin = margin(c(t = 50,
+                                                    b = 50)),
+                                  vjust = 10),
+        axis.text.x = element_text(family = "mono"),
+        axis.text.y = element_text(family = "mono"),
+        legend.title = element_text(family = "mono", 
+                                    face = "bold",
+                                    size = 7),
+        legend.text = element_text(family = "mono",
+                                   size = 6),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     size = 9,
+                                     vjust = 5),
+        legend.box.just = "left",
+        legend.box.background = element_rect())
+
+  scale_fill_discrete(limits = c("Republican", "Democrat", 
+                                      "Bipartisan, but mostly Republican", 
+                                      "Bipartisan", "N/A",
+                                      "Bipartisan, but mostly Democratic",
+                                      "Independent", 
+                                      "Mean Donations"))
+
+frequent %>% mutate(party = fct_relevel(Party, c("Republican", "Democrat", 
+                                      "Bipartisan, but mostly Republican", 
+                                      "Bipartisan", "N/A",
+                                      "Bipartisan, but mostly Democratic",
+                                      "Independent", 
+                                      "Mean Donations")))
+
+sum_donations <- frequent %>% group_by(Owner) %>%
+  summarise(sum = sum(amount)) %>%
+  rename(Sum = 'sum') %>%
+  arrange(desc(Sum))
+sum_donations
+
+pandoc.table(sum_donations, style = "grid")
 ```
 
-## Examining Top Donator 
+## Questions: How many donations, out of the 213 made by Charles Johnson, were made to which political parties? 
 ```{r}
@@
   mutate(party = fct_reorder(.f = Party, .x = n)) %>%
-   mutate(Party = fct_relevel(party, c("Republican", "Bipartisan, but mostly Republican",
-                                         "Democrat")))
+   mutate(Party = fct_relevel(party, c("Democrat", "Bipartisan, but mostly Republican", "Republican")))
 
-level_order2 <- factor(charles_johnson$Party, level = c('Republican', 'Democrat', 'Bipartisan, but mostly Republican'))
+level_order2 <- factor(charles_johnson$Party, level = c('Democrat', 'Bipartisan, but mostly Republican', 'Republican'))
 
@@
   geom_col() +
-  coord_flip() +
-  scale_fill_viridis_d(option = "plasma") +
+  scale_fill_viridis_d(option = "inferno") +
   labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
        x = " ",
-       y = "Count of Donations") +
+       y = " ") +
   theme(legend.position = "bottom",
@@
                                     face = "italic",
-                                    margin = margin(t = 20)))
+                                    margin = margin(t = 20)),
+        axis.title.y = element_text(family = "mono",
+                                    margin = margin(t = 20, b = 20, r = 20)))
 
-cj_party2 <- cj_party %>% select(n, party)
-
-ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
-  geom_col() + 
-  annotate(geom = "table") +
-  coord_flip()
+table_cjparty <- cj_party %>% arrange(desc(n)) %>%
+  select(Party, n) %>%
+  rename(Count = 'n')
+pandoc.table(table_cjparty)
 ```
 
-## What Are Some of These Organizations? 
+## Question: As we can see, most of the donations made by Charles Johnson were affiliated with the Republican party.
+What were some of these organizations and how many donations did Charles Johnson make to each of these organizations?
 ```{r}
@@
 
-## Organizations Receiving Most Donations Across All Leagues 
+## Questions: What are some organizations that seem to be recieving the most donations across all owners and leagues? What political party are these organizations affiliated with? 
 ```{r}
@@
 
-## Potential questions:
-## Who are the most recent top 10 billionaires: name v net worth ?
-
-## look at average age of billionaires in general/maybe by country?: do billionaires tend to be very old or are there more billionaires on the younger side?
-
-## Look at most prevalent industry of billionaires: mostly technology or something else?
-
-## How many billionaires in each country: mostly capitalist or other economic systems?
-
 ## Average networth of billionaires by industry?
 
-## Top 10 Billionaires coloured by industry (Forbes 2021 Billionaires)
+## Questions: Who were the billionaires with the top 10 highest net worths on the 2021 Forbes Billionaires List?
+How much are their net worths?
+What industry do they work in?
+Does any industry dominate the others?
 ```{r}
@@
 billionaires
+forbes_billionaires <- read_csv("data/forbes_billionaires.csv")
+forbes_billionaires
 
@@
 
-## Forbes Billionaire 2021 2.0 Data Set
+## Questions: What is the average age of the billionaires from the 10 countries with the most billionaires? Is there a pattern or do the averages widely differ? Are there any interesting outliers? 
 ```{r}
-forbes_billionaires <- read_csv("data/forbes_billionaires.csv")
-forbes_billionaires
-
-country <- forbes_billionaires %>% group_by(Country) %>%
-  summarise(n = n()) %>%
-  arrange(desc(n))
-country
-
 forbes_billionaires_age <- forbes_billionaires %>%
@@
            Country == "Italy") 
+countries_10
 
@@
 
-check <- countries_10 %>% filter(Age < 25 | Age > 90)
+check <- countries_10 %>% filter(age < 25 | age > 97)
+check
 
 filter <- countries_10 %>% filter(!is.na(age))
+filter
 filter2 <- filter %>% group_by(Country) %>%
-  summarise(Average = mean(age))
+  summarise(Average = mean(age)) %>%
+  mutate(order = fct_reorder(.f = Country, .x = Average))
+filter2
 
 ggplot(data = countries_10, aes(x = Country, y = age)) +
-  geom_point(alpha = 0.2) +
+  geom_point(alpha = 0.4) +
   coord_flip() +
-  geom_point(data = filter2, aes(y = Average, colour = "Mean Age"),
+  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age"),
              size = 2.5) +
@@
                                     size = 9,
-                                    face = "italic")) 
+                                    face = "italic")) +
+  geom_label_repel(data = check, aes(label = age, family = "mono"))
+```
+
+## Average net worth per industry 
+```{r}
+forbes_billionaires %>% group_by(Country) %>%
+  summarise(avg = mean(NetWorth))
+
+usa_df <- billionaires %>% filter(Country == "United States") %>% mutate(networth = parse_number(NetWorth)) 
+usa_df
+
+usa_df %>% group_by(Industry) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+usa_avg_df <- usa_df %>%
+   summarise(avg = mean(networth))
+usa_avg_df
+
+above_or_below_us <- usa_df %>% mutate(avg = mean(networth)) %>%
+  mutate(above_avg = if_else(networth > 6.08,
+                                      true = "ABOVE AVG",
+                                      false = "BELOW AVG")) %>%
+  filter(Industry == "Fashion & Retail") %>%
+  mutate(order = fct_reorder(.f = Name, .x = networth))
+above_or_below_us
+
+ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
+  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
+  geom_point() +
+  coord_flip() +
+  labs(x = "Name",
+      y = "Net Worth",
+      colour = "Average") +
+  theme(axis.text = element_text(family = "mono"),
+        axis.title = element_text(family = "mono"),
+        legend.text = element_text(family = "mono"),
+        legend.title = element_text(family = "mono"),
+        axis.ticks = element_blank())
+```
+
+## Questions: How many billionaires are there from the top 30 countries on the list? Do developed democracies have the most billionaires on the list?
+```{r}
+country <- forbes_billionaires %>% group_by(Country) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+country_30 <- country %>% slice(1:30) %>%
+  mutate(order = fct_reorder(.f = Country, .x = n))
+country_30
+
+ggplot(data = country_30, aes(x = order, y = n)) +
+  geom_point(colour = "orange") +
+  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
+  coord_flip() +
+  theme_light() +
+  theme(axis.ticks.x = element_blank()) +
+  labs(x = "Country", 
+       y = "Count of Billionaires",
+       title = "How Many Billionaires Are There From the Top 30 Countries?") +
+  theme(plot.title = element_text(family = "mono"),
+        axis.text = element_text(family = "mono"),
+        axis.title = element_text(family = "mono"))
 ```
@@
 ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
-  geom_point() +
+  geom_point(alpha = 0.4) +
+  coord_flip() +
+  labs(x = "Education Level",
+       y = "Net Worth")
+
+ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
+  geom_jitter(alpha = 0.4) +
   coord_flip() +
@@
 ```
-
-## Billionaires Age in Countries with most billionaires 
-```{r}
-
-ggplot(data = countries_10, aes(x = Country, y = Age)) +
-  geom_point() +
-  coord_flip() +
-  geom_point(data = average_top10_countries, aes(y = Average, colour = "Average Billionaire Age")) +
-  scale_colour_manual(values = c("Average Billionaire Age" = "red"))
-```
-
-## Blockbusters: A blockbuster is a Hollywood movie that's made with a large budget and big stars.
-A true blockbuster is extremely popular and brings in a lot of money (https://www.vocabulary.com/dictionary/blockbuster).
-```{r, message = FALSE, warning = FALSE, echo = FALSE}
-blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
-blockbusters
-```
-
-## Blockbuster Ratings: 1977 to 2019
-```{r, message = FALSE, warning = FALSE, echo = FALSE}
-blockbusters %>% group_by(mpaa_rating) %>%
-  summarise(n = n())
-
-blockbusters1 <- blockbusters %>% filter(!is.na(mpaa_rating)) %>%
-  rename(Film = 'film_title')
-
-ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
-                                          label = Film)) +
-  geom_point() +
-  facet_wrap(~mpaa_rating) +
-  geom_smooth(se = FALSE, method = 'lm') +
-  labs(y = "IMDB Rating",
-       x = "Release Year",
-       colour = "MPAA Rating",
-       title = "Blockbuster Ratings: 1977 to 2019") +
-  theme_hc() +
-  scale_colour_brewer(palette = "Dark2") +
-  theme(plot.title = element_text(family = "mono",
-                                  face = "italic",
-                                  margin = margin(t = 20, b = 20)),
-        axis.ticks = element_blank(),
-        axis.title = element_text(family = "mono",
-                                  face = "italic"),
-        axis.text = element_text(family = "mono"),
-        legend.box.background = element_rect(),
-        legend.text = element_text(family = "mono"),
-        legend.title = element_text(family = "mono",
-                                    face = "italic"),
-        axis.title.y = element_text(margin = margin(r = 20)),
-        axis.title.x = element_text(margin = margin(t = 20, b = 10)),
-        strip.text = element_text(family = "mono",
-                                  face = "bold"))
-
-blockbusters %>% group_by(mpaa_rating) %>%
-  summarise(n = n()) %>%
-  filter(!is.na(mpaa_rating))
-```
-
-## Has the Budget for Blockbusters Increased Throughout Time? 
-```{r}
-ggplot(data = blockbusters, aes(x = release_year, y = film_budget, colour = release_year)) +
-  geom_point() +
-  geom_smooth(se = FALSE, method = "lm", colour = "black") +
-  labs(x = "Release Year",
-       y = "Film Budget",
-       title = "Has the Budget for Blockbuster Films Increased Throughout Time?",
-       subtitle = "Film Budget for Blockbusters: 1977-2019") +
-  theme_bw() +
-  scale_colour_viridis_c() +
-  theme(legend.position = "none",
-        plot.title = element_text(family = "mono",
-                                  face = "bold",
-                                  margin = margin(c(t = 50, b = 50)),
-                                  vjust = 10),
-        plot.subtitle = element_text(family = "mono",
-                                     face = "italic",
-                                     vjust = 5),
-        axis.title = element_text(family = "mono",
-                                  face = "bold"),
-        axis.text = element_text(family = "mono"),
-        axis.ticks = element_blank(),
-        axis.title.x = element_text(margin = margin(c(l = 20))),
-        axis.title.y = element_text(margin = margin(c(t = 20, b = 20, r = 20)))) 
-## need to add more to this visualization 
-```
-
-## Which American/Domestic Distributor Has Produced the Most Blockbusters 1977-2019
-```{r}
-blockbusters3 <- blockbusters %>% group_by(domestic_distributor) %>%
-  summarise(n = n()) %>%
-  arrange(desc(n)) %>%
-  mutate(order = fct_reorder(.f = domestic_distributor, .x = n)) %>%
-  filter(!n == 1)
-
-ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
-  geom_point() +
-  geom_segment(aes(x = order, xend = order, y = 0, yend = n)) +
-  coord_flip() +
-  geom_label(data = blockbusters3, aes(label = n), show.legend = FALSE) +
-  labs(x = "Amount of Films Produced",
-       y = "Domestic Distributor",
-       title = "Amount of Blockbusters Produced by Domestic Distributors: 1977-2019") +
-  theme_bw() +
-  theme(legend.position = "none",
-        plot.title = element_text(family = "mono",
-                                  face = "bold",
-                                  margin = margin(c(t = 50)),
-                                  vjust = 10),
-        axis.title = element_text(family = "mono",
-                                  face = "bold"),
-        axis.text = element_text(family = "mono"),
-        axis.text.y = element_text(face = "italic"),
-        axis.ticks = element_blank(),
-        axis.title.x = element_text(margin = margin(c(b = 20))),
-        axis.title.y = element_text(margin = margin(c(t = 30, r = 30))))
-```
-
-## Work in Progress 
-```{r}
-blockbusters
-interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
-  select(rank, everything()) %>%
-  arrange(rank) %>%
-  slice(1:5) %>%
-  mutate(film_title = fct_recode(film_title, 
-                                 LOTR_The_Return_Of_The_King = "The Lord of the Rings: The Return of the King",
-                                 LOTR_Fellowship_Of_The_Ring = "The Lord of the Rings: The Fellowship of the Ring"))
-interest
-
-interest2 <- blockbusters %>% mutate(rank = rank(imdb_rating)) %>%
-  select(rank, everything()) %>%
-  arrange(rank) %>%
-  slice(1:5)
-interest2
-
-library(ggrepel)
-ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
-  geom_point(aes(colour = imdb_rating)) +
-  geom_label_repel(data = interest, aes(label = film_title)) +
-  geom_point(data = interest2, aes(x = release_year, y = domestic_gross, colour = imdb_rating)) +
-  geom_label_repel(data = interest2, aes(label = film_title))
-```
-
-## History of Rock
-```{r, message = FALSE, warning = FALSE, echo = FALSE}
-library(tidyverse)
-history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")
-history_of_rock
-```
-
-## Most Popular Nirvana Songs 
-```{r}
-history_of_rock %>% group_by(artist) %>%
-  summarise(n = n()) %>% arrange(desc(n))
-
-nirvana <- history_of_rock %>% rename(Popularity = 'popularity') %>%
-  filter(artist == "Nirvana") %>% arrange(desc(Popularity)) %>%
-  mutate(order = fct_reorder(.f = name, .x = Popularity)) %>%
-  rename(Release_Date = 'release_date')
-
-nirvana %>% select(order, everything())
-
-plot3 <- ggplot(data = nirvana, aes(x = order, y = Popularity, label = Popularity, colour = Popularity)) +
-  geom_point() +
-  geom_segment(aes(x = order, xend = order, y = 0, yend = Popularity)) +
-  coord_flip() +
-  labs(title = "Most Popular Nirvana Songs: 1991-2018",
-       colour = "Popularity", 
-       x = " ",
-       y = " ") +
-  theme_bw() +
-  scale_colour_viridis_b() +
-  theme(legend.position = "none")
-
-ggplotly(plot3, tooltip = "label")
-```
-
-## Trying to Make Density Ridges Plot 
-```{r}
-## install.packages("ggridges")
-library(ggridges)
-
-nirvana_small <- nirvana %>% slice(1:5) %>%
-  mutate(order = fct_reorder(.f = name, .x = valence))
-ggplot(data = nirvana_small, aes(x = order, y = valence)) +
-  geom_density_ridges() +
-  coord_flip() +
-  labs(x = "Title",
-       y = "Valence")
-```
-
-## Works in Progress - Simple Visualizations
-```{r}
-nirvana_line <- nirvana %>% rename(Title = 'name')
-plot10 <- ggplot(data = nirvana_line, aes(x = Release_Date, y = Popularity, label = Title)) +
-  geom_line() +
-  geom_point(colour = "darkolivegreen") +
-  labs(x = "Release Date",
-       y = "Popularity",
-       title = "Comparing Popularity by Release Date") +
-  theme_bw() +
-  theme(legend.position = "none")
-
-ggplotly(plot10, tooltip = "label")
-
-table <- history_of_rock %>% group_by(artist) %>%
-  summarise(mean = mean(popularity)) %>%
-  arrange(desc(mean)) %>%
-  slice(1:10)
-
-top10 <- history_of_rock %>% arrange(desc(popularity)) %>% slice(1:10)
-```
-
-## Unemployment Data Set
-```{r}
-library(lubridate)
-unemployment <- read_csv("data/unemployment_data_us.csv")
-ggplot(data = unemployment, aes(x = Date, y = Professional_Degree)) +
-  geom_point()
-```

### 2022-04-18 draft.Rmd
April 18th graded after class commit. Continued modifying visualizations and working on new ideas.

@@
         legend.box.background = element_rect())
+```
 
+## Only average - no political party 
+``` {r}
 ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
@@
         legend.box.background = element_rect())
+```
 
+## With average but no way to distinguish
+```{r}
 ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
   geom_point() +
-  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
+  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations"))+
   labs(title = "How Many Donations Have They Made?",
@@
                                       "Mean Donations")))
+```
 
+## sum of all donations
+```{r}
 sum_donations <- frequent %>% group_by(Owner) %>%
@@
   mutate(party = fct_reorder(.f = Party, .x = n)) %>%
-   mutate(Party = fct_relevel(party, c("Democrat", "Bipartisan, but mostly Republican", "Republican")))
+   mutate(Party = fct_relevel(party, c("Republican", "Bipartisan, but mostly Republican", "Democrat")))
 
@@
   geom_col() +
-  scale_fill_viridis_d(option = "inferno") +
+  coord_flip() +
+  scale_fill_brewer(palette= "Pastel2") +
   labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
@@
   labs(title = "Organizations Receiving Most Donations Among All Owners") +
-  scale_fill_brewer(palette = "Dark2") +
+  scale_fill_brewer(palette = "Accent") +
   theme(legend.position = "bottom") +
@@
                                                     b = 50)),
-                                  vjust = 10),
+                                  vjust = 7),
         axis.text = element_text(family = "mono"),
@@
         axis.title.x = element_text(size = 10,
-                                    margin = margin(t = 20,
+                                    margin = margin(t = 10,
                                                     b = 10)),
@@
   coord_flip() +
-  labs(x = "Billionaire Name", 
+  labs(x = "Billionaire", 
        y = "Net Worth",
@@
   scale_x_discrete(labels = new_names2) +
+  theme(legend.position = "bottom") +
   theme(axis.title = element_text(family = "mono",
-                                  face = "bold"),
+                                  face = "bold",
+                                  margin = margin(c(t = 30,
+                                                    b = 30))),
+        legend.box.spacing = unit(0.5, 'cm'),
         axis.text = element_text(family = "mono"),
@@
         plot.title = element_text(family = "mono",
-                                  face = "bold"),
+                                  face = "bold",
+                                  margin = margin(c(t = 15,
+                                                    b = 15,
+                                                    vjust = 15))),
+        legend.margin = margin(c(t = 30)),
         legend.title = element_text(family = "mono",
@@
         plot.caption = element_text(family = "mono",
-                                    face = "italic"))
+                                    face = "italic",
+                                    vjust = 45,
+                                    hjust = 0.5,
+                                    margin = margin(c(t = 30,
+                                                      b = 30))),
+        legend.key.size = unit(.3, 'cm'))
 ```
@@
   mutate(order = fct_reorder(.f = Country, .x = Average))
-filter2
+filter3 <- filter2 %>% rename(age = 'Average')
+```
 
+## Outliers labeled 
+```{r}
 ggplot(data = countries_10, aes(x = Country, y = age)) +
@@
   coord_flip() +
-  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age"),
+  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
              size = 2.5) +
+  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
+  labs(x = "Country", 
+       y = "Age",
+       title = "Average Age of Billionaires by Country") +
+  theme(legend.position = "bottom") +
+  theme(axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.ticks = element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(family = "mono",
+                                   face = "italic"), 
+        plot.caption = element_text(family = "mono",
+                                    size = 9,
+                                    face = "italic")) 
+```
+
+## Average labeled 
+```{r}
+ggplot(data = countries_10, aes(x = Country, y = age)) +
+  geom_point(alpha = 0.4) +
+  coord_flip() +
+  geom_label(data = filter3, aes(label = age)) +
   scale_colour_manual(values = c("Mean Age" = "red")) +
@@
        y = "Age",
-       title = "Average Age of Billionaires by Country",
-       caption = "The Red Points Indicate the Average Age of Billionaires From Each
-       Country") +
+       title = "Average Age of Billionaires by Country") +
   theme(axis.title = element_text(family = "mono",
@@
                                     size = 9,
-                                    face = "italic")) +
-  geom_label_repel(data = check, aes(label = age, family = "mono"))
+                                    face = "italic")) 
 ```
@@
       y = "Net Worth",
-      colour = "Average") +
+      caption = "Measured in Billions",
+      colour = "Average",
+      title = "Billionaires In The Fashion Industry",
+      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
   theme(axis.text = element_text(family = "mono"),
@@
         legend.title = element_text(family = "mono"),
+        plot.caption = element_text(family = "mono",
+                                    hjust = 0.5),
+        plot.title = element_text(family = "mono"),
+        plot.subtitle = element_text(family = "mono"),
         axis.ticks = element_blank())
@@
 
-## Playing Around with New Variables 
+## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
 ```{r}
@@
 
+harvard <- tidy_education %>% filter(University == "Harvard University")
+harvard
+
+## should do something with this to show the degree, self_made, networth, etc.
+
 tidy_education2 <- tidy_education %>% filter(Degree == "Bachelor of Arts/Science" |
@@
        y = "Net Worth")
+
+ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
+  geom_violin() +
+  coord_flip()
+
+library(ggridges)
+ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
+  geom_density_ridges()
 ```

### 2022-04-20 draft.Rmd
April 20th graded before class commit. Kept modifying components of theme for visualizations and worked on making a few more.

@@
                                  size = 8),
+        axis.text.x = element_text(face = "bold"),
         legend.box.background = element_rect(),
+        axis.ticks = element_blank(),
         legend.position = "bottom") 
@@
                                     face = "bold",
-                                    size = 5),
+                                    size = 8),
         legend.text = element_text(family = "mono",
-                                   size = 5),
+                                   size = 8),
         plot.subtitle = element_text(family = "mono",
@@
                                      size = 9),
+        axis.ticks = element_blank(),
         legend.box.background = element_rect())
@@
 ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
-  geom_col() +
+  geom_col(colour = "black") +
   coord_flip() +
@@
 ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
-  geom_col() +
+  geom_col(colour = "black") +
   coord_flip() +
@@
 ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
-  geom_col() +
+  geom_col(colour = "black") +
   coord_flip() +
-  labs(x = "Billionaire", 
+  labs(x = " ", 
        y = "Net Worth",
@@
                                                     b = 30))),
-        legend.box.spacing = unit(0.5, 'cm'),
         axis.text = element_text(family = "mono"),
+        axis.text.y = element_text(face = "bold"),
         axis.ticks = element_blank(),
@@
                                                     vjust = 15))),
-        legend.margin = margin(c(t = 30)),
+        axis.title.x = element_text(vjust = -3),
+        axis.title.y = element_text(vjust = 2),
+        legend.margin = margin(c(t = 30, b = 30)),
         legend.title = element_text(family = "mono",
@@
                                     face = "italic",
-                                    vjust = 45,
+                                    vjust = 35,
                                     hjust = 0.5,
@@
 filter3 <- filter2 %>% rename(age = 'Average')
+
+ggplot(data = countries_10, aes(x = Country, y = age)) +
+  geom_point(alpha = 0.4) +
+  coord_flip() +
+  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
+             size = 2.5) +
+  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
+  labs(x = "Country", 
+       y = "Age",
+       title = "Average Age of Billionaires by Country") +
+  theme(legend.position = "bottom") +
+  theme(axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.ticks = element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(family = "mono",
+                                   face = "italic"), 
+        plot.caption = element_text(family = "mono",
+                                    size = 9,
+                                    face = "italic")) 
 ```
@@
                                     size = 9,
-                                    face = "italic")) 
+                                    face = "italic")) +
+  geom_label_repel(data = check, aes(label = age))
 ```
@@
   geom_point() +
+  scale_colour_brewer(palette = "Accent") +
   coord_flip() +
-  labs(x = "Name",
+  labs(x = " ",
       y = "Net Worth",
@@
         legend.text = element_text(family = "mono"),
-        legend.title = element_text(family = "mono"),
+        legend.title = element_text(family = "mono",
+                                    face = "bold"),
         plot.caption = element_text(family = "mono",
                                     hjust = 0.5),
-        plot.title = element_text(family = "mono"),
-        plot.subtitle = element_text(family = "mono"),
-        axis.ticks = element_blank())
+        plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic"),
+        axis.title.x = element_text(face = "bold"),
+        axis.text.y = element_text(face = "italic",
+                                   vjust = 1),
+        axis.ticks = element_blank(),
+        legend.box.background = element_rect()) 
 ```
@@
         axis.title = element_text(family = "mono"))
+
+ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
+  geom_col(colour = "black") +
+  coord_flip() +
+  labs(x = " ", 
+       y = " ",
+       title = "How Many Billionaires Are There From the Top 30 Countries?",
+       fill = "Count") +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        axis.title = element_text(family = "mono"),
+        legend.title = element_text(family = "mono",
+                                    face = "bold"),
+        legend.text = element_text(family = "mono",
+                                   face = "italic"),
+        axis.ticks = element_blank()) +
+  scale_fill_viridis_b(n.breaks = 7) 
 ```
@@
 ```{r}
+forbes_billionaires %>% select(Self_made, everything())
 self_made <- forbes_billionaires %>% group_by(Self_made) %>%
-  summarise(n = n())
+  summarise(n = n()) %>%
+  filter(!is.na(Self_made))
 
-ggplot(data = forbes_billionaires, aes(x = Self_made)) +
-  geom_bar()
+ggplot(data = self_made, aes(x = Self_made, y = n, fill = Self_made)) +
+  geom_col(colour = "black") +
+  scale_fill_brewer(palette = "Spectral") +
+  labs(x = " ",
+       y = " ",
+       title = "How Many of These Billionaires Are Self-Made?",
+       fill = " ") +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  margin = margin(c(t = 30)),
+                                  vjust = 8,
+                                  size = 15),
+        legend.text = element_text(family = "mono"),
+        axis.text = element_text(family = "mono"),
+        axis.text.x = element_text(size = 15,
+                                   face = "bold"),
+        axis.ticks = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  geom_label(data = self_made, aes(label = n),
+              fill = "white",
+             label.size = 0.5) 
+```
 
+## Continuing to mess around 
+```{r}
 industry <- billionaires %>% group_by(Industry) %>%
@@
 combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))
-combined_billionaires
+
+combined_billionaires2 <- combined_billionaires %>% separate(col = Education, into = c("Degree", "University"),
+                                 sep = ", ")
+
+harvard <- combined_billionaires2 %>% filter(University == "Harvard University") 
+harvard
+
+harvard %>% group_by(Industry) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+ggplot(data = harvard, aes(x = Degree, y = NetWorth.x)) +
+  geom_point() +
+  coord_flip() +
+  geom_label(data = harvard, aes(label = Name))
+
+## should do something with this to show the degree, self_made, networth, etc.
 
@@
 
-harvard <- tidy_education %>% filter(University == "Harvard University")
-harvard
+tidy_education %>% filter(University == "Harvard University")
+```
 
-## should do something with this to show the degree, self_made, networth, etc.
-
+```{r}
 tidy_education2 <- tidy_education %>% filter(Degree == "Bachelor of Arts/Science" |
@@
 
-## Forbes Billionaire 2021 3.0 Data Set 
+## New Data Set
 ```{r}
-forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
-forbes_billionaires_geo 
+
 ```

### 2022-04-20 draft.Rmd
April 20th graded after class commit. Made a few changes and added some new visualizations.

@@
   scale_x_discrete(labels = new_names2) +
-  theme(legend.position = "bottom") +
   theme(axis.title = element_text(family = "mono",
@@
                                                     b = 15,
-                                                    vjust = 15))),
+                                                    vjust = 15)),
+                                  size = 15),
         axis.title.x = element_text(vjust = -3),
@@
         legend.title = element_text(family = "mono",
-                                    face = "bold"),
+                                    face = "bold",
+                                    size = 8),
         legend.text = element_text(family = "mono",
-                                   face = "italic"),
+                                   face = "italic",
+                                   size = 8),
         plot.caption = element_text(family = "mono",
                                     face = "italic",
-                                    vjust = 35,
+                                    vjust = 5,
                                     hjust = 0.5,
@@
                                     size = 9,
-                                    face = "italic")) 
+                                    face = "italic"),
+  legend.box.background = element_rect())
 ```
@@
 ```{r}
+
+countries10_2 <- countries_10 %>% mutate()
+
 ggplot(data = countries_10, aes(x = Country, y = age)) +
-  geom_point(alpha = 0.4) +
+  geom_point(alpha = 0.4, size = 1.5) +
   coord_flip() +
   geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
-             size = 2.5) +
+             size = 2.5, shape = 8) +
   scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
@@
                                     face = "italic")) +
-  geom_label_repel(data = check, aes(label = age))
+  theme(legend.position = "none") +
+  geom_label_repel(data = check, aes(label = age)) +
+  geom_text_repel(data = check, aes(label = Name, fontface = "bold"), size = 2) +
+  geom_text_repel(data = check, aes(label = Source))
 ```
@@
         plot.title = element_text(family = "mono",
-                                  face = "bold"),
+                                  face = "bold",
+                                  margin = margin(c(t = 10, b = 10))),
         plot.subtitle = element_text(family = "mono",
-                                     face = "italic"),
-        axis.title.x = element_text(face = "bold"),
-        axis.text.y = element_text(face = "italic",
-                                   vjust = 1),
+                                     face = "italic",
+                                     margin = margin(c(t = 10, b = 10)),
+                                     vjust = 2),
+        axis.title.x = element_text(face = "bold",
+                                    margin = margin(c(t = 10, b = 10))),
+        axis.text.y = element_text(face = "italic"),
         axis.ticks = element_blank(),
@@
   theme(axis.ticks.x = element_blank()) +
-  labs(x = "Country", 
-       y = "Count of Billionaires",
+  labs(x = " ", 
+       y = " ",
        title = "How Many Billionaires Are There From the Top 30 Countries?") +
@@
         axis.text = element_text(family = "mono"),
-        axis.title = element_text(family = "mono"))
+        axis.title = element_text(family = "mono")) +
+  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.1, size = 3.2, colour = "black")
 
@@
         axis.title = element_text(family = "mono"),
-        legend.title = element_text(family = "mono",
-                                    face = "bold"),
-        legend.text = element_text(family = "mono",
-                                   face = "italic"),
-        axis.ticks = element_blank()) +
-  scale_fill_viridis_b(n.breaks = 7) 
+        legend.title = element_text(family = "mono"),
+        legend.text = element_text(family = "mono"),
+        axis.ticks = element_blank(),
+        legend.position = "none") +
+  scale_fill_viridis_b(n.breaks = 6) +
+  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.1, size = 3, colour = "black")
 ```
 
-## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
+## usa billionaires
+```{r}
+library(plotly)
+us_forbes_billionaires <- combined_billionaires %>% filter(Country.x == "United States")
+us_forbes_billionaires
+
+us_forbes_billionaires %>% group_by(Industry) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+plot10 <- ggplot(data = us_forbes_billionaires, aes(x = NetWorth.x, y = Age.x,
+                                                    label = Name, colour = Industry)) +
+  geom_jitter() +
+  labs(x = "NetWorth",
+       y = "Age",
+       title = "Billionaires in the U.S.") +
+  theme(plot.title = element_text(face = "bold",
+                                  size = 15,
+                                  margin = margin(c(t = 10, b = 10))),
+        axis.ticks = element_blank(),
+        legend.title = element_text(face = "bold"),
+        axis.title = element_text(face = "bold"))
+
+ggplotly(plot10, tooltip = "label")
+```
+
+## How many are self-made (from entire list) ? 
 ```{r}
@@
   geom_point() +
-  coord_flip() +
-  geom_label(data = harvard, aes(label = Name))
+  coord_flip()
 

### 2022-04-25 draft.Rmd
April 25th graded before class commit. Found a new data set and worked on style component of project.

--- 2022-04-18 draft.Rmd
@@
 ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
-  geom_point(size = 2) +
+  geom_point(size = 3) +
   labs(x = " ", 
@@
                                   face = "bold",
-                                  size = 15,
+                                  size = 18,
                                   margin = margin(c(t = 20,
                                                     b = 50,
-                                                    vjust = 10))),
+                                                    vjust = 15))),
         plot.subtitle = element_text(family = "mono",
                                      face = "italic",
-                                     size = 10),
+                                     size = 15,
+                                     vjust = 2.5),
         legend.title = element_text(family = "mono",
@@
                                  size = 8),
+        axis.text.x = element_text(face = "bold"),
+        axis.text.y = element_text(face = "bold"),
         legend.box.background = element_rect(),
+        axis.ticks = element_blank(),
+        legend.key.size = unit(1.3, 'cm'),
         legend.position = "bottom") 
@@
                                   face = "bold",
-                                  size = 12),
-        axis.text.x = element_text(family = "mono"),
-        axis.text.y = element_text(family = "mono"),
+                                  size = 18,
+                                   margin = margin(c(t = 20,
+                                                    b = 50,
+                                                    vjust = 15))),
+        axis.text.x = element_text(family = "mono",
+                                   face = "bold"),
+        axis.text.y = element_text(family = "mono",
+                                   face = "bold"),
         legend.title = element_text(family = "mono", 
                                     face = "bold",
-                                    size = 5),
+                                    size = 10),
         legend.text = element_text(family = "mono",
-                                   size = 5),
+                                   size = 8),
         plot.subtitle = element_text(family = "mono",
                                      face = "italic",
-                                     size = 9),
+                                     size = 15,
+                                     vjust = 2.5),
+        axis.ticks = element_blank(),
+        legend.key.size = unit(0.8, 'cm'),
         legend.box.background = element_rect())
@@
 
-## Only average - no political party 
-``` {r}
-ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
-  geom_point() +
-  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
-  labs(title = "How Many Donations Have They Made?",
-       subtitle = "Examining The Monetary Amount of Observed Political Donations",
-       y = " ",
-       x = " ",
-       colour = "Party") +
-  scale_colour_brewer(palette = "Dark2") +
-  scale_colour_manual(values = c("Mean Donations" = "red")) +
-    theme_bw() +
-  theme(legend.position = "bottom",
-        plot.title = element_text(family = "mono",
-                                  face = "bold",
-                                  size = 12,
-                                  margin = margin(c(t = 50,
-                                                    b = 50)),
-                                  vjust = 10),
-        axis.text.x = element_text(family = "mono"),
-        axis.text.y = element_text(family = "mono"),
-        legend.title = element_text(family = "mono", 
-                                    face = "bold",
-                                    size = 7),
-        legend.text = element_text(family = "mono",
-                                   size = 6),
-        plot.subtitle = element_text(family = "mono",
-                                     face = "italic",
-                                     size = 9,
-                                     vjust = 5),
-        legend.box.just = "left",
-        legend.box.background = element_rect())
-```
-
-## With average but no way to distinguish
-```{r}
-ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
-  geom_point() +
-  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations"))+
-  labs(title = "How Many Donations Have They Made?",
-       subtitle = "Examining The Monetary Amount of Observed Political Donations",
-       y = " ",
-       x = " ",
-       colour = "Party") +
-  scale_colour_viridis_d() +
-    theme_bw() +
-  theme(legend.position = "bottom",
-        plot.title = element_text(family = "mono",
-                                  face = "bold",
-                                  size = 12,
-                                  margin = margin(c(t = 50,
-                                                    b = 50)),
-                                  vjust = 10),
-        axis.text.x = element_text(family = "mono"),
-        axis.text.y = element_text(family = "mono"),
-        legend.title = element_text(family = "mono", 
-                                    face = "bold",
-                                    size = 7),
-        legend.text = element_text(family = "mono",
-                                   size = 6),
-        plot.subtitle = element_text(family = "mono",
-                                     face = "italic",
-                                     size = 9,
-                                     vjust = 5),
-        legend.box.just = "left",
-        legend.box.background = element_rect())
-
-  scale_fill_discrete(limits = c("Republican", "Democrat", 
-                                      "Bipartisan, but mostly Republican", 
-                                      "Bipartisan", "N/A",
-                                      "Bipartisan, but mostly Democratic",
-                                      "Independent", 
-                                      "Mean Donations"))
-
-frequent %>% mutate(party = fct_relevel(Party, c("Republican", "Democrat", 
-                                      "Bipartisan, but mostly Republican", 
-                                      "Bipartisan", "N/A",
-                                      "Bipartisan, but mostly Democratic",
-                                      "Independent", 
-                                      "Mean Donations")))
-```
-
-## sum of all donations
+## Question: What is the sum of all of the donations made by these owners? 
 ```{r}
@@
                                   hjust = 0.5,
-                                  size = 13,
+                                  size = 18,
                                   margin = margin(c(t = 50,
@@
                                   vjust = 10),
-        axis.text = element_text(family = "mono"),
+        axis.text = element_text(family = "mono",
+                                 face = "bold"),
         legend.title = element_text(family = "mono",
@@
         axis.title.y = element_text(family = "mono",
-                                    margin = margin(t = 20, b = 20, r = 20)))
+                                    margin = margin(t = 20, b = 20, r = 20)),
+        legend.key.size = unit(0.8, 'cm'),
+        legend.box.background = element_rect())
 
@@
 ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
-  geom_col() +
+  geom_col(colour = "black") +
   coord_flip() +
   labs(x = " ",
-       y = "Count of Donations") +
+       y = " ") +
   labs(title = "Organizations Receiving Most Donations Among All Owners") +
@@
                                   face = "bold",
-                                  margin = margin(c(t = 50,
-                                                    b = 50)),
-                                  vjust = 7),
-        axis.text = element_text(family = "mono"),
+                                  margin = margin(c(t = 40,
+                                                    b = 40)),
+                                  vjust = 7,
+                                  size = 18),
+        axis.text = element_text(family = "mono",
+                                 face = "bold"),
         axis.title = element_text(family = "mono",
@@
                                     face = "bold"),
-        legend.text = element_text(family = "mono"),
+        legend.text = element_text(family = "mono",
+                                   face = "bold"),
         axis.ticks = element_blank(),
-         legend.box.background = element_rect())
+        legend.key.size = unit(1, 'cm'),
+         legend.box.background = element_rect()) +
+    geom_text(data = recipients, aes(label = n, fontface = "bold"), size = 5, hjust = -0.25)
 
@@
        colour = "Industry",
-       title = "2021 Forbes Billionaires with the Highest Net Worth") +
+       title = "2021 Forbes Billionaires",
+       subtitle = "Examining the Billionaires with the Highest Net Worth from 2021") +
   scale_fill_viridis_d() +
   scale_x_discrete(labels = new_names2) +
-  theme(legend.position = "bottom") +
+  theme(legend.position = c(0.9, 0.18)) +
   theme(axis.title = element_text(family = "mono",
@@
                                                     b = 15,
-                                                    vjust = 15))),
-        legend.margin = margin(c(t = 30)),
+                                                    vjust = 15)),
+                                  size = 20),
+        plot.subtitle = element_text(family = "mono",
+                                     size = 12,
+                                     face = "italic",
+                                       vjust = 2.5),
+        axis.title.x = element_text(vjust = -3,
+                                    size = 15),
+        axis.title.y = element_text(vjust = 2),
         legend.title = element_text(family = "mono",
-                                    face = "bold"),
+                                    face = "bold",
+                                    size = 15),
         legend.text = element_text(family = "mono",
-                                   face = "italic"),
+                                   face = "italic",
+                                   size = 10),
         plot.caption = element_text(family = "mono",
                                     face = "italic",
-                                    vjust = 45,
+                                    vjust = 3,
                                     hjust = 0.5,
                                     margin = margin(c(t = 30,
-                                                      b = 30))),
-        legend.key.size = unit(.3, 'cm'))
+                                                      b = 30)),
+                                    size = 14),
+        legend.key.width = unit(1, 'cm'),
+        legend.key.height = unit(1, 'cm'),
+  legend.box.background = element_rect())
 ```
@@
 
-check <- countries_10 %>% filter(age < 25 | age > 97)
-check
+outliers_age <- countries_10 %>% filter(age < 25 | age > 97)
+outliers_age
 
-filter <- countries_10 %>% filter(!is.na(age))
-filter
-filter2 <- filter %>% group_by(Country) %>%
+countries_10_no_missing_values <- countries_10 %>% filter(!is.na(age))
+countries_10_no_missing_values
+
+countries_10_average_age <- filter %>% group_by(Country) %>%
   summarise(Average = mean(age)) %>%
+  arrange(desc(Average)) %>% 
   mutate(order = fct_reorder(.f = Country, .x = Average))
-filter3 <- filter2 %>% rename(age = 'Average')
+countries_10_average_age
+
+countries_10_average_age %>% arrange(desc(Average))
+countries_10_average_age %>% arrange(Average)
+
+level_order3 <- factor(countries_10$Country, level = c('China',
+                                                                   'Russia',
+                                                                   'Brazil',
+                                                                   'Germany',
+                                                                   'Canada',
+                                                                   'Hong Kong',
+                                                                   'United States',
+                                                                   'United Kingdom',
+                                                                   'India',
+                                                       'Italy'))
+
+ggplot(data = countries_10, aes(x = level_order3, y = age)) +
+  geom_point(alpha = 0.7, colour = "goldenrod1") +
+  coord_flip() +
+  geom_point(data = countries_10_average_age, aes(x = Country, y = Average, colour = "Mean Age of Billionaires"),
+             size = 6,
+             shape = 18) +
+  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
+  labs(x = " ", 
+       y = " ",
+       title = "Average Age of Billionaires by Country") +
+  theme(legend.position = "bottom") +
+  theme(axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        axis.text.y = element_text(face = "bold"),
+        axis.text.x = element_text(face = "bold"),
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 18,
+                                  margin = margin(c(t = 50,
+                                                    b = 50)),
+                                  vjust = 10),
+        axis.ticks = element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(family = "mono",
+                                   face = "bold"), 
+        plot.caption = element_text(family = "mono",
+                                    size = 9,
+                                    face = "italic"),
+        legend.key.size = unit(1.2, 'cm'),
+  legend.box.background = element_rect())
 ```
@@
 ggplot(data = countries_10, aes(x = Country, y = age)) +
-  geom_point(alpha = 0.4) +
+  geom_point(alpha = 0.4, size = 1.5, colour = "goldenrod1") +
   coord_flip() +
@@
              size = 2.5) +
-  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
+  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
   labs(x = "Country", 
@@
                                     size = 9,
-                                    face = "italic")) 
+                                    face = "italic")) +
+  theme(legend.position = "none") +
+    geom_label_repel(data = outliers_age, aes(label = age))
+
+  ggplot(data = countries_10, aes(x = level_order3, y = age)) +
+  geom_point(alpha = 0.7, colour = "goldenrod1") +
+  coord_flip() +
+  geom_point(data = countries_10_average_age, aes(x = Country, y = Average, colour = "Mean Age of Billionaires"),
+             size = 6,
+             shape = 18) +
+  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
+  labs(x = " ", 
+       y = " ",
+       title = "Average Age of Billionaires by Country") +
+  theme(legend.position = "bottom") +
+  theme(axis.title = element_text(family = "mono",
+                                  face = "bold"),
+        axis.text = element_text(family = "mono"),
+        axis.text.y = element_text(face = "bold"),
+        axis.text.x = element_text(face = "bold"),
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 18,
+                                  margin = margin(c(t = 50,
+                                                    b = 50)),
+                                  vjust = 10),
+        axis.ticks = element_blank(),
+        legend.title = element_blank(),
+        legend.text = element_text(family = "mono",
+                                   face = "bold"), 
+        plot.caption = element_text(family = "mono",
+                                    size = 9,
+                                    face = "italic"),
+        legend.key.size = unit(1.2, 'cm'),
+  legend.box.background = element_rect()) 
 ```
@@
         axis.title = element_text(family = "mono"),
-        legend.text = element_text(family = "mono"),
-        legend.title = element_text(family = "mono"),
+        legend.text = element_text(family = "mono",
+                                   face = "bold"),
+        legend.title = element_text(family = "mono",
+                                    face = "bold",
+                                    size = 10),
         plot.caption = element_text(family = "mono",
-                                    hjust = 0.5),
-        plot.title = element_text(family = "mono"),
-        plot.subtitle = element_text(family = "mono"),
-        axis.ticks = element_blank())
+                                    hjust = 0.5,
+                                    size = 15, 
+                                    vjust = 1,
+                                    margin = margin(c(t = 10,
+                                                      b = 20))),
+        plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  margin = margin(c(t = 20,
+                                                    b = 20)),
+                                  vjust = 2.5, 
+                                  size = 20),
+        plot.subtitle = element_text(family = "mono",
+                                     face = "italic",
+                                     margin = margin(c(t = 10, b = 10)),
+                                     vjust = 2.5,
+                                     size = 15),
+        axis.title.x = element_text(face = "bold",
+                                    margin = margin(c(t = 10, b = 10)),
+                                    size = 15),
+        axis.text.y = element_text(face = "italic",
+                                   size = 10),
+        axis.ticks = element_blank(),
+        legend.box.background = element_rect(),
+        legend.position = c(0.885, 0.2),
+         legend.key.width = unit(5, 'cm'),
+        legend.key.height = unit(3, 'cm'))
 ```
@@
   theme(axis.ticks.x = element_blank()) +
-  labs(x = "Country", 
-       y = "Count of Billionaires",
+  labs(x = " ", 
+       y = " ",
        title = "How Many Billionaires Are There From the Top 30 Countries?") +
-  theme(plot.title = element_text(family = "mono"),
-        axis.text = element_text(family = "mono"),
-        axis.title = element_text(family = "mono"))
+  theme(plot.title = element_text(family = "mono",
+                                  size = 20,
+                                  face = "bold",
+                                   margin = margin(c(t = 40,
+                                                    b = 50)),
+                                  vjust = 5),
+        axis.text = element_text(family = "mono",
+                                 face = "bold"),
+        axis.title = element_text(family = "mono")) +
+  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
 ```
 
-## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
+## bar plot
 ```{r}
+ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
+  geom_col(colour = "black") +
+  coord_flip() +
+  labs(x = " ", 
+       y = " ",
+       title = "How Many Billionaires Are There From the Top 30 Countries?",
+       fill = "Count") +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  size = 20,
+                                   margin = margin(c(t = 40,
+                                                    b = 50)),
+                                  vjust = 5),
+        axis.text = element_text(family = "mono",
+                                 face = "bold"),
+        axis.title = element_text(family = "mono"),
+        legend.title = element_text(family = "mono"),
+        legend.text = element_text(family = "mono"),
+        axis.ticks = element_blank(),
+        legend.position = "none") +
+  scale_fill_viridis_b(n.breaks = 6) +
+  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
+```
+
+## How many are self-made (from entire list) ? 
+```{r}
+forbes_billionaires %>% select(Self_made, everything())
 self_made <- forbes_billionaires %>% group_by(Self_made) %>%
-  summarise(n = n())
+  summarise(n = n()) %>%
+  filter(!is.na(Self_made))
 
-ggplot(data = forbes_billionaires, aes(x = Self_made)) +
-  geom_bar()
+ggplot(data = self_made, aes(x = Self_made, y = n, fill = Self_made)) +
+  geom_col(colour = "black") +
+  scale_fill_brewer(palette = "Spectral") +
+  labs(x = " ",
+       y = " ",
+       title = "How Many of These Billionaires Are Self-Made?",
+       fill = " ") +
+  theme(plot.title = element_text(family = "mono",
+                                  face = "bold",
+                                  margin = margin(c(t = 30)),
+                                  vjust = 8,
+                                  size = 20),
+        legend.text = element_text(family = "mono"),
+        axis.text = element_text(family = "mono"),
+        axis.text.x = element_text(size = 15,
+                                   face = "bold"),
+        axis.ticks = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  geom_label(data = self_made, aes(label = n),
+              fill = "white",
+             label.size = 0.5) 
+```
 
+## Continuing to mess around 
+```{r}
 industry <- billionaires %>% group_by(Industry) %>%
@@
 combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))
-combined_billionaires
+
+combined_billionaires2 <- combined_billionaires %>% separate(col = Education, into = c("Degree", "University"),
+                                 sep = ", ")
+
+harvard <- combined_billionaires2 %>% filter(University == "Harvard University") 
+harvard
+
+harvard %>% group_by(Industry) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+ggplot(data = harvard, aes(x = Degree, y = NetWorth.x)) +
+  geom_point() +
+  coord_flip()
+
+## should do something with this to show the degree, self_made, networth, etc.
 
@@
 
-harvard <- tidy_education %>% filter(University == "Harvard University")
-harvard
-
-## should do something with this to show the degree, self_made, networth, etc.
+tidy_education %>% filter(University == "Harvard University")
 
@@
   coord_flip()
-
-library(ggridges)
-ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
-  geom_density_ridges()
 ```
 
-## Forbes Billionaire 2021 3.0 Data Set 
+## usa billionaires
 ```{r}
+library(plotly)
+us_forbes_billionaires <- combined_billionaires %>% filter(Country.x == "United States")
+us_forbes_billionaires
+
+us_forbes_billionaires %>% group_by(Industry) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+plot10 <- ggplot(data = us_forbes_billionaires, aes(x = NetWorth.x, y = Age.x,
+                                                    label = Name, colour = Industry)) +
+  geom_jitter() +
+  labs(x = "NetWorth",
+       y = "Age",
+       title = "Billionaires in the U.S.") +
+  theme(plot.title = element_text(face = "bold",
+                                  size = 15,
+                                  margin = margin(c(t = 10, b = 10))),
+        axis.ticks = element_blank(),
+        legend.title = element_text(face = "bold"),
+        axis.title = element_text(face = "bold"))
+
+ggplotly(plot10, tooltip = "label")
+```
+
+## Map
+```{r}
+library(maps)
+library(tidyverse)
+state_df <- ggplot2::map_data("state")
+
 forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
-forbes_billionaires_geo 
+forbes_billionaires_geo %>% select(geometry, everything())
+forbes_billionaires_geo %>% separate(col = geometry, into = c(""))
 ```
+
+## New Data Set
+```{r}
+pvp_dataset <- read_csv("data/pvp_dataset.csv")
+pvp_dataset
+
+ggplot(data = pvp_dataset, aes(x = year, y = salary)) +
+  geom_line()
+pvp_dataset_2 <- read_csv("data/pvp_dataset 2.csv")
+pvp_dataset_2
+```

### 2022-04-25 draft.Rmd
April 25th graded after class commit. Worked on setting up blogdown and connecting to Git. Worked briefly on creating new visualizations.

@@
   geom_point(data = countries_10_average_age, aes(x = Country, y = Average, colour = "Mean Age of Billionaires"),
-             size = 6,
-             shape = 18) +
+             size = 4) +
   scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
@@
 
-ggplot(data = country_30, aes(x = order, y = n)) +
-  geom_point(colour = "orange") +
-  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
-  coord_flip() +
-  theme_light() +
-  theme(axis.ticks.x = element_blank()) +
-  labs(x = " ", 
-       y = " ",
-       title = "How Many Billionaires Are There From the Top 30 Countries?") +
-  theme(plot.title = element_text(family = "mono",
-                                  size = 20,
-                                  face = "bold",
-                                   margin = margin(c(t = 40,
-                                                    b = 50)),
-                                  vjust = 5),
-        axis.text = element_text(family = "mono",
-                                 face = "bold"),
-        axis.title = element_text(family = "mono")) +
-  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
-```
-
-## bar plot
-```{r}
 ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
@@
 
-## Continuing to mess around 
+## Make just one more visualization that makes sense 
 ```{r}
@@
 
-## Map
+## Try to make the Map
 ```{r}
@@
 ## New Data Set
+
+## Potential questions:
+
+## How has President salary changed over time
+
+## Is there a predominant party or evenly split
+
+## How much more do presidents make compared to vice presidents
+
+## Has salary ever increased from term to term 
 ```{r}
@@
   geom_line()
+
 pvp_dataset_2 <- read_csv("data/pvp_dataset 2.csv")
 pvp_dataset_2
+
+pres_salary <- pvp_dataset_2 %>% filter(position_title == "PRESIDENT OF THE UNITED STATES")
+pres_salary
+
+ggplot(data = pres_salary, aes(x = year, y = salary)) +
+  geom_line()
+
+ggplot(data = pres_salary, aes(x = year, y = salary, colour = salary)) +
+  geom_line()
+
+pres_salary %>% group_by(party) %>%
+  summarise(n = n()) %>%
+  arrange(desc(n))
+
+ggplot(data = pres_salary, aes(x = salary, y = party)) +
+  geom_point()
+
+ggplot(data = pres_salary, aes(x = , y = party, colour = salary)) +
+  geom_point()
 ```
